---
title: "Rent & Roster"
subtitle: "Can college-age renters actually afford to live in the U.S.?"

author:
  - "Elma M."
  - "Partner 1"
  - "Partner 2"

date: today

format:
  html:
    page-layout: full
    toc: false
---

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

library(tidycensus)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(plotly)
library(leaflet)
library(tigris)
library(sf)
library(scales)
library(forcats)
library(htmltools)

readRenviron("~/.Renviron")
options(tigris_use_cache = TRUE)
```

```{r}
#| label: load-data
#| echo: false
#| message: false
#| warning: false
#| cache: true

years <- c(2015, 2016, 2017, 2018, 2019, 2021, 2022, 2023)

income_by_age_raw <- map_dfr(years, function(yr) {
  get_acs(
    geography = "state",
    variables = c(
      "under25"  = "B19049_002",
      "age25_44" = "B19049_003"
    ),
    year   = yr,
    survey = "acs1"
  ) %>%
    mutate(year = yr)
})

rent_raw <- map_dfr(years, function(yr) {
  get_acs(
    geography = "state",
    variables = "B25064_001",
    year   = yr,
    survey = "acs1"
  ) %>%
    mutate(year = yr)
})

income_2023 <- income_by_age_raw %>%
  filter(year == 2023) %>%
  select(State = NAME, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate) %>%
  rename(income_under25 = under25, income_25_44 = age25_44)

rent_2023 <- rent_raw %>%
  filter(year == 2023) %>%
  select(State = NAME, median_rent_monthly = estimate) %>%
  mutate(median_rent_annual = median_rent_monthly * 12)

burden_2023 <- income_2023 %>%
  inner_join(rent_2023, by = "State") %>%
  filter(State != "Puerto Rico") %>%
  mutate(
    burden_under25 = (median_rent_annual / income_under25) * 100,
    burden_cat_under25 = case_when(
      burden_under25 < 30  ~ "Affordable",
      burden_under25 < 50  ~ "Burdened",
      burden_under25 >= 50 ~ "Severely Burdened"
    ),
    burden_25_44 = (median_rent_annual / income_25_44) * 100,
    burden_cat_25_44 = case_when(
      burden_25_44 < 30  ~ "Affordable",
      burden_25_44 < 50  ~ "Burdened",
      burden_25_44 >= 50 ~ "Severely Burdened"
    )
  ) %>%
  arrange(desc(burden_under25))
```

```{=html}
<style>
.hero {
  background: linear-gradient(135deg, #0f0c29, #302b63, #24243e);
  color: white; padding: 80px 40px; text-align: center;
  margin: -20px -20px 40px -20px; border-radius: 0 0 20px 20px;
}
.hero h1 { font-size: 3.5em; font-weight: 900; margin: 0 0 10px 0; letter-spacing: -1px; }
.hero p { font-size: 1.3em; opacity: 0.85; max-width: 600px; margin: 0 auto 30px auto; }
.stats-row { display: flex; justify-content: center; gap: 40px; flex-wrap: wrap; margin-top: 40px; }
.stat-box {
  background: rgba(255,255,255,0.1); border: 1px solid rgba(255,255,255,0.2);
  border-radius: 16px; padding: 24px 32px; text-align: center; min-width: 160px;
}
.stat-number { font-size: 3em; font-weight: 900; color: #e74c3c; display: block; line-height: 1; }
.stat-label { font-size: 0.85em; opacity: 0.8; margin-top: 6px; line-height: 1.4; }
.section-title {
  font-size: 2em; font-weight: 800; color: #1a1a2e;
  margin: 50px 0 10px 0; border-left: 5px solid #e74c3c; padding-left: 16px;
}
.section-subtitle { color: #666; font-size: 1.1em; margin-bottom: 24px; padding-left: 21px; }
.calc-container {
  background: linear-gradient(135deg, #1a1a2e, #16213e);
  border-radius: 20px; padding: 40px; color: white; margin: 20px 0;
}
.calc-title { font-size: 1.5em; font-weight: 800; margin: 0 0 8px 0; }
.calc-subtitle { opacity: 0.7; margin-bottom: 30px; font-size: 0.95em; }
.calc-inputs { display: flex; gap: 16px; flex-wrap: wrap; margin-bottom: 20px; }
.calc-input-group { flex: 1; min-width: 200px; }
.calc-input-group label { display: block; font-size: 0.85em; font-weight: 600; margin-bottom: 8px; opacity: 0.8; text-transform: uppercase; }
.calc-input-group input, .calc-input-group select {
  width: 100%; padding: 14px 16px; border: 2px solid rgba(255,255,255,0.2);
  border-radius: 10px; font-size: 15px; box-sizing: border-box;
  background: rgba(255,255,255,0.1); color: white; outline: none;
}
.calc-input-group input::placeholder { color: rgba(255,255,255,0.4); }
.calc-input-group select option { background: #1a1a2e; }
.calc-btn {
  background: #e74c3c; color: white; border: none;
  padding: 14px 36px; border-radius: 10px; font-size: 16px;
  font-weight: 700; cursor: pointer; transition: all 0.2s;
}
.calc-btn:hover { background: #c0392b; transform: translateY(-1px); }
.result-gauge { margin-top: 30px; display: none; }
.result-details { background: rgba(255,255,255,0.08); border-radius: 12px; padding: 20px; margin-top: 16px; }
.result-verdict { font-size: 1.1em; line-height: 1.6; margin-bottom: 12px; }
.result-rent-line { font-size: 0.85em; opacity: 0.6; }
.story-section { padding: 40px 0; border-bottom: 1px solid #eee; max-width: 700px; }
.story-section:last-child { border-bottom: none; }
.big-number { font-size: 5em; font-weight: 900; color: #e74c3c; line-height: 1; margin-bottom: 10px; }
.conclusion-grid { display: grid; grid-template-columns: repeat(auto-fit, minmax(220px, 1fr)); gap: 20px; margin: 30px 0; }
.conclusion-card { background: #f8f9fa; border-radius: 16px; padding: 24px; border-top: 4px solid #e74c3c; }
.conclusion-card h4 { margin: 0 0 10px 0; color: #1a1a2e; font-size: 1em; }
.conclusion-card p { margin: 0; color: #555; font-size: 0.9em; line-height: 1.6; }
</style>

<div class="hero">
  <h1>Can You Afford to Rent?</h1>
  <p>A data investigation into student housing affordability across all 50 U.S. states</p>
  <div class="stats-row">
    <div class="stat-box">
      <span class="stat-number" id="c1">0</span>
      <div class="stat-label">states burden<br>young renters</div>
    </div>
    <div class="stat-box">
      <span class="stat-number" id="c2">0%</span>
      <div class="stat-label">average burden<br>for under-25</div>
    </div>
    <div class="stat-box">
      <span class="stat-number" id="c3">0</span>
      <div class="stat-label">states burden<br>ages 25-44</div>
    </div>
    <div class="stat-box">
      <span class="stat-number" id="c4">0x</span>
      <div class="stat-label">higher burden<br>young vs older</div>
    </div>
  </div>
</div>

<script>
function animCount(id, target, suffix, dur) {
  const el = document.getElementById(id);
  let v = 0;
  const step = target / (dur / 16);
  const t = setInterval(() => {
    v += step;
    if (v >= target) { el.textContent = target + suffix; clearInterval(t); }
    else { el.textContent = Math.floor(v) + suffix; }
  }, 16);
}
window.addEventListener("load", () => {
  setTimeout(() => {
    animCount("c1", 34, "", 1500);
    animCount("c2", 34, "%", 1500);
    animCount("c3", 0, "", 500);
    animCount("c4", 2, "x", 1000);
  }, 400);
});
function getColor(r) {
  if (r < 30) return "#27ae60";
  if (r < 50) return "#e67e22";
  return "#e74c3c";
}
function drawGauge(ratio, containerId) {
  const color = getColor(ratio);
  const angle = Math.min((ratio / 60) * 180, 180);
  const rad = (angle - 180) * Math.PI / 180;
  const x = 100 + 80 * Math.cos(rad);
  const y = 100 + 80 * Math.sin(rad);
  const el = document.getElementById(containerId);
  if (!el) return;
  el.innerHTML = `<svg width="200" height="110" viewBox="0 0 200 110">
    <path d="M 20 100 A 80 80 0 0 1 180 100" fill="none" stroke="#eee" stroke-width="16" stroke-linecap="round"/>
    <path d="M 20 100 A 80 80 0 0 1 180 100" fill="none" stroke="${color}" stroke-width="16"
      stroke-linecap="round" stroke-dasharray="${angle * 80 * Math.PI / 180} 1000"/>
    <line x1="100" y1="100" x2="${x}" y2="${y}" stroke="#1a1a2e" stroke-width="3" stroke-linecap="round"/>
    <circle cx="100" cy="100" r="5" fill="#1a1a2e"/>
    <text x="100" y="72" text-anchor="middle" font-size="22" font-weight="900" fill="${color}">${ratio}%</text>
    <text x="20" y="112" font-size="9" fill="#999">0%</text>
    <text x="88" y="22" font-size="9" fill="#999">30%</text>
    <text x="170" y="112" font-size="9" fill="#999">60%</text>
  </svg>`;
}
</script>
```

<div class="section-title">The Map: Rent Burden and Universities</div>
<div class="section-subtitle">States colored by rent burden for under-25 renters. Click any graduation cap pin to see how affordable that state is for students.</div>

```{r}
#| label: university-map
#| echo: false
#| message: false
#| warning: false

universities <- data.frame(
  name = c(
    "UCLA", "UC Berkeley", "Stanford University", "USC",
    "University of Miami", "Florida State University", "University of Florida",
    "NYU", "Columbia University", "Cornell University",
    "University of Texas Austin", "Texas A&M", "Rice University",
    "University of Michigan", "Michigan State University",
    "University of Washington", "University of Colorado Boulder",
    "Arizona State University", "University of Arizona",
    "Georgia Tech", "University of Georgia",
    "University of Maryland", "Georgetown University",
    "University of Hawaii Manoa",
    "Indiana University", "Purdue University",
    "University of Minnesota", "University of Wisconsin Madison",
    "Iowa State University", "University of Iowa",
    "University of Oregon", "Oregon State University",
    "Penn State University", "University of Pennsylvania",
    "University of North Carolina", "NC State University",
    "Louisiana State University", "Tulane University",
    "University of Alabama", "Auburn University",
    "University of Kentucky", "University of Louisville",
    "West Virginia University", "University of Virginia",
    "University of Nevada Las Vegas",
    "University of New Mexico",
    "University of Montana",
    "University of Wyoming",
    "University of Vermont",
    "University of Rhode Island", "University of Connecticut",
    "University of South Carolina", "Clemson University",
    "University of Tennessee", "Vanderbilt University",
    "University of Arkansas",
    "University of Oklahoma", "Oklahoma State University",
    "University of Nebraska Lincoln",
    "University of North Dakota", "North Dakota State University",
    "Kansas State University", "University of Kansas",
    "University of Mississippi", "Mississippi State University",
    "University of Delaware",
    "University of South Dakota", "South Dakota State University",
    "University of Maine", "University of Idaho",
    "University of Alaska Fairbanks",

    # Added colleges
    "Macalester College",
    "Harvard University",
    "MIT",
    "Boston University",
    "Yale University",
    "Princeton University",
    "University of Chicago",
    "Carnegie Mellon University",
    "University of Pittsburgh",
    "Ohio State University",
    "University of Illinois Urbana-Champaign",
    "Northwestern University",
    "Boston College",
    "Rutgers University",
    "Temple University",
    "Drexel University",
    "George Washington University",
    "American University",
    "Emory University",
    "University of Central Florida"
  ),

  lat = c(
    34.0689, 37.8724, 37.4275, 34.0224,
    25.7142, 30.4420, 29.6465,
    40.7295, 40.8075, 42.4534,
    30.2849, 30.6187, 29.7174,
    42.2780, 42.7009,
    47.6553, 40.0076,
    33.4255, 32.2319,
    33.7756, 33.9480,
    38.9869, 38.9076,
    21.2969,
    39.1682, 40.4259,
    44.9740, 43.0753,
    42.0140, 41.6611,
    44.0460, 44.5646,
    40.7982, 39.9526,
    35.9049, 35.7847,
    30.4133, 29.9384,
    33.2148, 32.6099,
    38.0473, 38.2527,
    39.6350, 38.0336,
    36.1140,
    35.0844,
    46.8625,
    42.8666,
    44.4759,
    41.4801, 41.8084,
    33.9979, 34.6834,
    35.9546, 36.1447,
    36.0671,
    35.2076, 36.1156,
    40.8202,
    47.9219, 46.8974,
    39.1836, 38.9543,
    34.3648, 33.4554,
    39.6784,
    43.0760, 44.3168,
    44.9015, 46.7196,
    64.8581,

    # Added colleges
    44.9375,
    42.3770,
    42.3601,
    42.3505,
    41.3163,
    40.3430,
    41.7886,
    40.4444,
    40.4440,
    40.0076,
    40.1020,
    42.0565,
    42.3355,
    40.5008,
    39.9812,
    39.9566,
    38.8997,
    38.9378,
    33.7925,
    28.6024
  ),

  lng = c(
    -118.4452, -122.2595, -122.1697, -118.2851,
    -80.2790, -84.2980, -82.3520,
    -73.9965, -73.9626, -76.4735,
    -97.7341, -96.3365, -95.4019,
    -83.7382, -84.4821,
    -122.3035, -105.2659,
    -111.9400, -110.9501,
    -84.3963, -83.3776,
    -76.9426, -77.0735,
    -157.8167,
    -86.5230, -86.9081,
    -93.2350, -89.4012,
    -93.6465, -91.5550,
    -123.0694, -123.2780,
    -77.8600, -75.1932,
    -79.0469, -78.6785,
    -91.1800, -90.1183,
    -87.5450, -85.4808,
    -84.5047, -85.7585,
    -79.9559, -78.5080,
    -115.1398,
    -106.6504,
    -114.0120,
    -108.9658,
    -73.1937,
    -71.5274, -72.2495,
    -81.0219, -82.8374,
    -83.9274, -86.8025,
    -94.1792,
    -97.4395, -96.5925,
    -96.7005,
    -101.9971, -96.7833,
    -96.5717, -95.2483,
    -89.5377, -88.7873,
    -75.7497,
    -96.9040, -96.8022,
    -68.9675, -116.9190,
    -147.8469,

    # Added colleges
    -93.1710,
    -71.1167,
    -71.0942,
    -71.1054,
    -72.9223,
    -74.6514,
    -87.5987,
    -79.9532,
    -79.9959,
    -83.0300,
    -88.2272,
    -87.6753,
    -71.1668,
    -74.4474,
    -75.1557,
    -75.1899,
    -77.0479,
    -77.0881,
    -84.3267,
    -81.2001
  ),

  state = c(
    "California", "California", "California", "California",
    "Florida", "Florida", "Florida",
    "New York", "New York", "New York",
    "Texas", "Texas", "Texas",
    "Michigan", "Michigan",
    "Washington", "Colorado",
    "Arizona", "Arizona",
    "Georgia", "Georgia",
    "Maryland", "District of Columbia",
    "Hawaii",
    "Indiana", "Indiana",
    "Minnesota", "Wisconsin",
    "Iowa", "Iowa",
    "Oregon", "Oregon",
    "Pennsylvania", "Pennsylvania",
    "North Carolina", "North Carolina",
    "Louisiana", "Louisiana",
    "Alabama", "Alabama",
    "Kentucky", "Kentucky",
    "West Virginia", "Virginia",
    "Nevada",
    "New Mexico",
    "Montana",
    "Wyoming",
    "Vermont",
    "Rhode Island", "Connecticut",
    "South Carolina", "South Carolina",
    "Tennessee", "Tennessee",
    "Arkansas",
    "Oklahoma", "Oklahoma",
    "Nebraska",
    "North Dakota", "North Dakota",
    "Kansas", "Kansas",
    "Mississippi", "Mississippi",
    "Delaware",
    "South Dakota", "South Dakota",
    "Maine", "Idaho",
    "Alaska",

    # Added colleges
    "Minnesota",
    "Massachusetts",
    "Massachusetts",
    "Massachusetts",
    "Connecticut",
    "New Jersey",
    "Illinois",
    "Pennsylvania",
    "Pennsylvania",
    "Ohio",
    "Illinois",
    "Illinois",
    "Massachusetts",
    "New Jersey",
    "Pennsylvania",
    "Pennsylvania",
    "District of Columbia",
    "District of Columbia",
    "Georgia",
    "Florida"
  )
) %>%
  left_join(
    burden_2023 %>% select(State, burden_under25, burden_cat_under25,
                           median_rent_annual, income_under25),
    by = c("state" = "State")
  ) %>%
  mutate(
    bg_color = case_when(
      burden_under25 < 30 ~ "#d4edda",
      burden_under25 < 50 ~ "#fff3cd",
      TRUE                ~ "#f8d7da"
    ),
    txt_color = case_when(
      burden_under25 < 30 ~ "#155724",
      burden_under25 < 50 ~ "#856404",
      TRUE                ~ "#721c24"
    ),
    popup_text = paste0(
      "<div style='font-family:sans-serif;min-width:240px;padding:4px;'>",
      "<div style='font-size:1.1em;font-weight:800;color:#1a1a2e;margin-bottom:4px;'>", name, "</div>",
      "<div style='font-size:0.82em;color:#888;margin-bottom:10px;'>", state, "</div>",
      "<div style='background:", bg_color, ";padding:12px;border-radius:10px;margin-bottom:10px;text-align:center;'>",
      "<div style='font-size:2em;font-weight:900;color:", txt_color, ";'>", round(burden_under25, 1), "%</div>",
      "<div style='font-size:0.78em;color:", txt_color, ";'>rent burden for under-25 renters</div>",
      "</div>",
      "<div style='font-size:0.85em;line-height:1.8;'>",
      "<b>Annual Rent:</b> $", format(round(median_rent_annual), big.mark = ","), "<br>",
      "<b>Under-25 Income:</b> $", format(round(income_under25), big.mark = ","), "<br>",
      "<b>Category:</b> <span style='font-weight:700;color:", txt_color, ";'>", burden_cat_under25, "</span>",
      "</div></div>"
    ),
    marker_color = case_when(
      burden_under25 < 30 ~ "green",
      burden_under25 < 50 ~ "orange",
      TRUE                ~ "red"
    )
  )

states_sf2 <- tigris::states(cb = TRUE, resolution = "20m", year = 2022) %>%
  filter(!STUSPS %in% c("PR", "GU", "VI", "MP", "AS")) %>%
  sf::st_transform(crs = 4326) %>%
  left_join(burden_2023, by = c("NAME" = "State"))

pal2 <- colorNumeric(
  palette = c("#27ae60", "#f39c12", "#e74c3c"),
  domain  = c(10, 55)
)

icon_green  <- makeAwesomeIcon(icon = "graduation-cap", library = "fa",
                               markerColor = "green",  iconColor = "white")
icon_orange <- makeAwesomeIcon(icon = "graduation-cap", library = "fa",
                               markerColor = "orange", iconColor = "white")
icon_red    <- makeAwesomeIcon(icon = "graduation-cap", library = "fa",
                               markerColor = "red",    iconColor = "white")

unis_g <- universities %>% filter(marker_color == "green")
unis_o <- universities %>% filter(marker_color == "orange")
unis_r <- universities %>% filter(marker_color == "red")

m <- leaflet(states_sf2) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(
    fillColor   = ~pal2(burden_under25),
    fillOpacity = 0.65,
    color       = "white",
    weight      = 1,
    smoothFactor = 0.5,
    label = ~paste0(NAME, ": ", round(burden_under25, 1), "% burden") %>%
      lapply(htmltools::HTML),
    labelOptions = labelOptions(
      style = list("font-weight" = "bold", padding = "4px 8px"),
      textsize = "12px"
    )
  ) %>%
  addLegend(
    pal = pal2, values = ~burden_under25,
    title = "Rent Burden (%)<br><small>Under-25 Householders</small>",
    position = "bottomleft",
    labFormat = labelFormat(suffix = "%")
  )

if (nrow(unis_g) > 0) {
  m <- m %>% addAwesomeMarkers(
    data = unis_g, lng = ~lng, lat = ~lat,
    icon = icon_green, popup = ~popup_text,
    label = ~name, group = "Affordable States"
  )
}
if (nrow(unis_o) > 0) {
  m <- m %>% addAwesomeMarkers(
    data = unis_o, lng = ~lng, lat = ~lat,
    icon = icon_orange, popup = ~popup_text,
    label = ~name, group = "Burdened States"
  )
}
if (nrow(unis_r) > 0) {
  m <- m %>% addAwesomeMarkers(
    data = unis_r, lng = ~lng, lat = ~lat,
    icon = icon_red, popup = ~popup_text,
    label = ~name, group = "Severely Burdened States"
  )
}

m %>%
  addLayersControl(
    overlayGroups = c("Affordable States", "Burdened States", "Severely Burdened States"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  setView(lng = -96, lat = 38, zoom = 4)
```

<div class="section-title">The Generational Gap</div>
<div class="section-subtitle">Every established adult is affordable. Two thirds of young renters are not.</div>

```{r}
#| label: gen-gap
#| echo: false
#| message: false
#| warning: false

burden_long <- burden_2023 %>%
  select(State, burden_under25, burden_25_44) %>%
  pivot_longer(c(burden_under25, burden_25_44),
               names_to = "age_group", values_to = "burden_ratio") %>%
  mutate(age_group = recode(age_group,
    "burden_under25" = "Under 25 (college-age)",
    "burden_25_44"   = "Ages 25-44 (established adults)"
  ))

p4 <- ggplot(burden_long,
  aes(x = burden_ratio, fill = age_group,
      text = paste0(age_group, "<br>Burden: ", round(burden_ratio, 1), "%"))) +
  geom_histogram(bins = 20, color = "white", linewidth = 0.3,
                 alpha = 0.82, position = "identity") +
  geom_vline(xintercept = 30, linetype = "dashed", color = "#1a1a2e", linewidth = 1) +
  geom_vline(xintercept = 50, linetype = "dashed", color = "#c0392b", linewidth = 1) +
  annotate("rect", xmin = 30, xmax = 50, ymin = 0, ymax = Inf, alpha = 0.05, fill = "#e67e22") +
  annotate("rect", xmin = 50, xmax = Inf, ymin = 0, ymax = Inf, alpha = 0.08, fill = "#c0392b") +
  annotate("text", x = 31, y = 16, label = "Burdened zone", hjust = 0,
           size = 3.2, color = "#e67e22", fontface = "italic") +
  annotate("text", x = 51, y = 16, label = "Severely burdened", hjust = 0,
           size = 3.2, color = "#c0392b", fontface = "italic") +
  scale_fill_manual(values = c(
    "Under 25 (college-age)"          = "#e74c3c",
    "Ages 25-44 (established adults)" = "#3498db"
  ), name = "Age Group") +
  scale_x_continuous(labels = label_percent(scale = 1)) +
  labs(x = "Rent Burden Ratio", y = "Number of States",
       caption = "Source: ACS 1-Year Estimates (B19049, B25064), 2023") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "top", panel.grid.minor = element_blank())

ggplotly(p4, tooltip = "text") %>%
  layout(legend = list(orientation = "h", x = 0.05, y = 1.12),
         font = list(family = "sans-serif"))
```

```{=html}
<div class="story-section">
  <div class="big-number">34</div>
  <p style="font-size:1.2em;color:#333;line-height:1.7;">Out of 51 states, <strong>34 place young renters in the cost-burdened category</strong>. In two thirds of the country, a typical under-25 householder spends more than 30 cents of every dollar on rent alone.</p>
</div>
<div class="story-section">
  <div class="big-number">0</div>
  <p style="font-size:1.2em;color:#333;line-height:1.7;">The number of states where adults aged 25-44 are cost-burdened. <strong>Not a single one.</strong> The same rents that crush young budgets are entirely manageable once income catches up.</p>
</div>
<div class="story-section">
  <div class="big-number">2x</div>
  <p style="font-size:1.2em;color:#333;line-height:1.7;">Young renters spend roughly <strong>twice as much of their income on rent</strong> as established adults. Average 33.7% for under-25 versus 17.8% for 25-44. Same apartments. Very different realities.</p>
</div>
```

<div class="section-title">Your Personal Calculator</div>
<div class="section-subtitle">Find out exactly where you stand based on your actual income.</div>

```{r}
#| label: calculator
#| echo: false
#| results: asis

rent_json <- paste0(
  "{",
  paste0('"', burden_2023$State, '":', round(burden_2023$median_rent_annual, 0),
         collapse = ","),
  "}"
)

cat(paste0(
'<div class="calc-container">
<div class="calc-title">Student Housing Affordability Calculator</div>
<div class="calc-subtitle">Enter your annual income and pick a state to see your personal rent burden</div>

<div class="calc-inputs">
<div class="calc-input-group">
<label>Your Annual Income ($)</label>
<input type="number" id="ci" placeholder="e.g. 28000"/>
</div>

<div class="calc-input-group">
<label>Select a State</label>
<select id="cs"><option value="">Choose a state...</option></select>
</div>
</div>

<button class="calc-btn" onclick="runCalc()">Calculate My Burden</button>

<div class="result-gauge" id="rg">
<div style="text-align:center"><div id="cg"></div></div>
<div class="result-details">
<div class="result-verdict" id="rv"></div>
<div class="result-rent-line" id="rl"></div>
</div>
</div>
</div>

<script>
const CRD = ', rent_json, ';
const csel = document.getElementById("cs");

Object.keys(CRD).sort().forEach(s => {
  const o = document.createElement("option");
  o.value = s;
  o.textContent = s;
  csel.appendChild(o);
});

function runCalc() {
  const income = parseFloat(document.getElementById("ci").value);
  const state  = document.getElementById("cs").value;
  const gDiv   = document.getElementById("rg");

  if (!income || income <= 0 || !state) {
    gDiv.style.display = "block";
    document.getElementById("rv").innerHTML =
      "<span style=\'color:#f39c12\'>Please enter income and select a state.</span>";
    document.getElementById("rl").textContent = "";
    document.getElementById("cg").innerHTML = "";
    return;
  }

  const rent  = CRD[state];
  const ratio = parseFloat(((rent / income) * 100).toFixed(1));

  gDiv.style.display = "block";

  let verdict;
  if (ratio < 30) {
    verdict = "At <strong>" + ratio + "%</strong> of your income on rent in " + state + ", you fall below the 30% threshold. You have room to save and breathe.";
  } else if (ratio < 50) {
    verdict = "In " + state + ", <strong>" + ratio + "%</strong> of your income goes to rent. That leaves less than 70 cents of every dollar for everything else.";
  } else {
    verdict = "In " + state + ", a staggering <strong>" + ratio + "%</strong> of your income would go to rent. This is a crisis-level burden by every economic standard.";
  }

  document.getElementById("rv").innerHTML = verdict;
  document.getElementById("rl").textContent =
    "Based on median annual rent of $" + rent.toLocaleString() + " in " + state + " (ACS 2023)";
  drawGauge(ratio, "cg");
}
</script>'
))
```

<div class="section-title">Should I Go There?</div>
<div class="section-subtitle">Enter your income, pick a college, and find out if you can actually afford to live there. We will also find you cheaper alternatives.</div>

```{r}
#| label: should-i-go-there-tool
#| echo: false
#| results: asis

college_tool_data <- universities %>%
  select(
    college_name = name,
    state
  ) %>%
  left_join(
    burden_2023 %>%
      select(
        State,
        median_rent_annual,
        income_under25,
        burden_under25,
        burden_cat_under25
      ),
    by = c("state" = "State")
  ) %>%
  distinct(college_name, .keep_all = TRUE) %>%
  arrange(college_name)

umn_row <- college_tool_data %>%
  filter(college_name == "University of Minnesota")

if (nrow(umn_row) == 0) {
  umn_row <- college_tool_data %>%
    filter(grepl("Minnesota", college_name))
}

umn_rent <- round(umn_row$median_rent_annual[1], 0)

college_json <- paste0(
  "{",
  paste0(
    '"', gsub('"', '\\\\"', college_tool_data$college_name), '":{',
    '"state":"', gsub('"', '\\\\"', college_tool_data$state), '",',
    '"rent":', round(college_tool_data$median_rent_annual, 0), ',',
    '"income_under25":', round(college_tool_data$income_under25, 0), ',',
    '"state_burden":', round(college_tool_data$burden_under25, 1), ',',
    '"category":"', gsub('"', '\\\\"', as.character(college_tool_data$burden_cat_under25)), '"',
    "}",
    collapse = ","
  ),
  "}"
)

state_json <- paste0(
  "[",
  paste0(
    "{",
    '"state":"', gsub('"', '\\\\"', burden_2023$State), '",',
    '"rent":', round(burden_2023$median_rent_annual, 0), ',',
    '"burden":', round(burden_2023$burden_under25, 1),
    "}",
    collapse = ","
  ),
  "]"
)

cat(paste0('<style>
.go-college-wrap{
background:linear-gradient(135deg,#111827,#1f2937,#0f172a);
color:white;
border-radius:24px;
padding:36px;
margin:30px 0;
box-shadow:0 18px 50px rgba(0,0,0,0.18);
}
.go-college-title{
font-size:2em;
font-weight:900;
margin-bottom:8px;
}
.go-college-subtitle{
color:rgba(255,255,255,0.78);
margin-bottom:26px;
font-size:1em;
line-height:1.6;
max-width:760px;
}
.go-college-grid{
display:grid;
grid-template-columns:repeat(auto-fit,minmax(230px,1fr));
gap:16px;
margin-bottom:20px;
}
.go-field label{
display:block;
font-size:0.82em;
font-weight:700;
letter-spacing:0.06em;
text-transform:uppercase;
color:rgba(255,255,255,0.72);
margin-bottom:8px;
}
.go-field input,
.go-field select{
width:100%;
box-sizing:border-box;
padding:14px 16px;
border-radius:12px;
border:2px solid rgba(255,255,255,0.14);
background:rgba(255,255,255,0.08);
color:white;
font-size:15px;
outline:none;
}
.go-field select option{
color:black;
}
.go-btn-row{
display:flex;
gap:12px;
flex-wrap:wrap;
margin-top:6px;
}
.go-btn{
border:none;
border-radius:12px;
padding:14px 22px;
font-weight:800;
font-size:15px;
cursor:pointer;
transition:0.2s ease;
}
.go-btn-primary{
background:#ef4444;
color:white;
}
.go-btn-primary:hover{
background:#dc2626;
transform:translateY(-1px);
}
.go-btn-secondary{
background:#f8fafc;
color:#111827;
}
.go-btn-secondary:hover{
background:#e2e8f0;
transform:translateY(-1px);
}
.go-results{
display:none;
margin-top:28px;
}
.go-top{
display:grid;
grid-template-columns:260px 1fr;
gap:24px;
align-items:center;
}
@media (max-width:800px){
.go-top{
grid-template-columns:1fr;
}
}
.go-card{
background:rgba(255,255,255,0.08);
border:1px solid rgba(255,255,255,0.1);
border-radius:18px;
padding:22px;
}
.go-badge{
display:inline-block;
padding:7px 12px;
border-radius:999px;
font-size:0.8em;
font-weight:800;
margin-top:10px;
}
.go-verdict{
font-size:1.14em;
line-height:1.7;
margin-bottom:14px;
}
.go-mini{
color:rgba(255,255,255,0.7);
font-size:0.92em;
line-height:1.6;
}
.go-compare-box{
margin-top:18px;
background:rgba(255,255,255,0.06);
border-left:5px solid #f59e0b;
border-radius:14px;
padding:16px 18px;
}
.go-compare-title{
font-size:0.83em;
letter-spacing:0.06em;
text-transform:uppercase;
color:rgba(255,255,255,0.7);
font-weight:800;
margin-bottom:8px;
}
.go-compare-text{
font-size:1.02em;
line-height:1.65;
}
.go-extra-box{
margin-top:18px;
background:rgba(255,255,255,0.06);
border-left:5px solid #60a5fa;
border-radius:14px;
padding:16px 18px;
}
.go-extra-title{
font-size:0.83em;
letter-spacing:0.06em;
text-transform:uppercase;
color:rgba(255,255,255,0.7);
font-weight:800;
margin-bottom:8px;
}
.go-extra-text{
font-size:1.02em;
line-height:1.65;
}
.go-alt-results{
display:none;
margin-top:22px;
}
.go-alt-title{
font-size:1.1em;
font-weight:800;
margin-bottom:12px;
}
.go-alt-grid{
display:grid;
grid-template-columns:repeat(auto-fit,minmax(210px,1fr));
gap:14px;
}
.go-alt-card{
background:rgba(255,255,255,0.08);
border:1px solid rgba(255,255,255,0.1);
border-radius:16px;
padding:16px;
}
.go-alt-college{
font-weight:800;
font-size:1em;
margin-bottom:5px;
}
.go-alt-state{
color:rgba(255,255,255,0.72);
font-size:0.9em;
margin-bottom:10px;
}
.go-alt-metric{
font-size:0.96em;
line-height:1.6;
}
.go-note{
margin-top:14px;
color:rgba(255,255,255,0.65);
font-size:0.88em;
line-height:1.5;
}
.go-move-wrap{
margin-top:30px;
padding-top:24px;
border-top:1px solid rgba(255,255,255,0.12);
}
.go-move-title{
font-size:1.3em;
font-weight:900;
margin-bottom:8px;
}
.go-move-subtitle{
color:rgba(255,255,255,0.72);
margin-bottom:18px;
line-height:1.6;
}
.go-move-results{
display:none;
margin-top:18px;
}
.go-move-grid{
display:grid;
grid-template-columns:repeat(auto-fit,minmax(210px,1fr));
gap:14px;
}
.go-pill{
display:inline-block;
padding:4px 10px;
border-radius:999px;
font-size:0.78em;
font-weight:800;
margin-top:8px;
}
</style>

<div class="go-college-wrap">
<div class="go-college-title">Should I Go There?</div>
<div class="go-college-subtitle">
Type your annual income, choose a university, and see whether living in that state would actually be affordable for you.
You will also get a comparison with the University of Minnesota, the income needed to become affordable, and a stress test if rent rises by 10%.
</div>

<div class="go-college-grid">
<div class="go-field">
<label>Your Annual Income ($)</label>
<input type="number" id="go-income" placeholder="e.g. 28000" />
</div>
<div class="go-field">
<label>Select a College</label>
<select id="go-college">
<option value="">Choose a college...</option>
</select>
</div>
</div>

<div class="go-btn-row">
<button class="go-btn go-btn-primary" onclick="runCollegeAffordabilityTool()">Check Affordability</button>
<button class="go-btn go-btn-secondary" onclick="findAffordableAlternatives()">Best College Alternatives</button>
</div>

<div class="go-results" id="go-results">
<div class="go-top">
<div class="go-card">
<div id="go-gauge"></div>
</div>

<div class="go-card">
<div class="go-verdict" id="go-verdict"></div>
<div id="go-badge-wrap"></div>
<div class="go-mini" id="go-details"></div>

<div class="go-compare-box">
<div class="go-compare-title">Comparison</div>
<div class="go-compare-text" id="go-compare"></div>
</div>

<div class="go-extra-box">
<div class="go-extra-title">Income needed</div>
<div class="go-extra-text" id="go-income-needed"></div>
</div>

<div class="go-extra-box">
<div class="go-extra-title">What if rent rises by 10%?</div>
<div class="go-extra-text" id="go-rent-shock"></div>
</div>
</div>
</div>
</div>

<div class="go-alt-results" id="go-alt-results">
<div class="go-alt-title">Best college alternatives for your income</div>
<div class="go-alt-grid" id="go-alt-grid"></div>
<div class="go-note">
These are the lowest-burden college options in your current list, ranked for your income.
</div>
</div>

<div class="go-move-wrap">
<div class="go-move-title">Where Should I Move?</div>
<div class="go-move-subtitle">
Enter your income and we will rank the best U.S. states for affordability based on median annual rent.
</div>
<div class="go-btn-row">
<button class="go-btn go-btn-secondary" onclick="recommendStates()">Find Best States For Me</button>
</div>
<div class="go-move-results" id="go-move-results">
<div class="go-move-grid" id="go-move-grid"></div>
</div>
</div>
</div>

<script>
const COLLEGE_DATA = ', college_json, ';
const STATE_DATA = ', state_json, ';
const UMN_RENT = ', umn_rent, ';

const collegeSelect = document.getElementById("go-college");
Object.keys(COLLEGE_DATA).sort().forEach(college => {
const opt = document.createElement("option");
opt.value = college;
opt.textContent = college;
collegeSelect.appendChild(opt);
});

function burdenColor(ratio) {
if (ratio < 30) return "#22c55e";
if (ratio < 50) return "#f59e0b";
return "#ef4444";
}

function burdenLabel(ratio) {
if (ratio < 30) return "Affordable";
if (ratio < 50) return "Stretch";
return "Very hard";
}

function badgeHTML(ratio) {
const color = burdenColor(ratio);
return `<span class="go-badge" style="background:${color}; color:white;">${burdenLabel(ratio)}</span>`;
}

function movePill(ratio) {
if (ratio < 30) return `<span class="go-pill" style="background:#22c55e;color:white;">Affordable</span>`;
if (ratio < 50) return `<span class="go-pill" style="background:#f59e0b;color:white;">Stretch</span>`;
return `<span class="go-pill" style="background:#ef4444;color:white;">Very hard</span>`;
}

function drawCollegeGauge(ratio) {
const capped = Math.min(ratio, 60);
const angle = (capped / 60) * 180;
const rad = (angle - 180) * Math.PI / 180;
const x = 100 + 78 * Math.cos(rad);
const y = 100 + 78 * Math.sin(rad);
const color = burdenColor(ratio);

return `
<svg width="220" height="130" viewBox="0 0 220 130">
<path d="M 30 100 A 70 70 0 0 1 190 100"
fill="none" stroke="#e5e7eb" stroke-width="16" stroke-linecap="round"/>
<path d="M 30 100 A 70 70 0 0 1 190 100"
fill="none" stroke="${color}" stroke-width="16" stroke-linecap="round"
stroke-dasharray="${angle * 70 * Math.PI / 180} 1000"/>
<line x1="110" y1="100" x2="${x + 10}" y2="${y}" stroke="#111827" stroke-width="3" stroke-linecap="round"/>
<circle cx="110" cy="100" r="5" fill="#111827"/>
<text x="110" y="70" text-anchor="middle" font-size="24" font-weight="900" fill="${color}">
${ratio.toFixed(1)}%
</text>
<text x="30" y="118" font-size="10" fill="#9ca3af">0%</text>
<text x="103" y="22" font-size="10" fill="#9ca3af">30%</text>
<text x="178" y="118" font-size="10" fill="#9ca3af">60%</text>
</svg>`;
}

function currency(x) {
return "$" + Math.round(x).toLocaleString();
}

function runCollegeAffordabilityTool() {
const income = parseFloat(document.getElementById("go-income").value);
const college = document.getElementById("go-college").value;

const results = document.getElementById("go-results");
const verdict = document.getElementById("go-verdict");
const details = document.getElementById("go-details");
const compare = document.getElementById("go-compare");
const gauge = document.getElementById("go-gauge");
const badgeWrap = document.getElementById("go-badge-wrap");
const incomeNeededBox = document.getElementById("go-income-needed");
const rentShockBox = document.getElementById("go-rent-shock");

if (!income || income <= 0 || !college) {
results.style.display = "block";
verdict.innerHTML = "<span style=\'color:#fbbf24;\'>Please enter your income and choose a college.</span>";
details.innerHTML = "";
compare.innerHTML = "";
gauge.innerHTML = "";
badgeWrap.innerHTML = "";
incomeNeededBox.innerHTML = "";
rentShockBox.innerHTML = "";
return;
}

const info = COLLEGE_DATA[college];
const yourRatio = (info.rent / income) * 100;
const umnRatio = (UMN_RENT / income) * 100;
const diff = yourRatio - umnRatio;
const neededIncome = info.rent / 0.30;
const incomeGap = Math.max(0, neededIncome - income);
const shockRent = info.rent * 1.10;
const shockRatio = (shockRent / income) * 100;

let verdictText = "";
if (yourRatio < 30) {
verdictText = `If you chose <strong>${college}</strong>, about <strong>${yourRatio.toFixed(1)}%</strong> of your income would go to rent. That falls below the standard 30% affordability threshold.`;
} else if (yourRatio < 50) {
verdictText = `If you chose <strong>${college}</strong>, about <strong>${yourRatio.toFixed(1)}%</strong> of your income would go to rent. That means housing would take a large share of your budget.`;
} else {
verdictText = `If you chose <strong>${college}</strong>, about <strong>${yourRatio.toFixed(1)}%</strong> of your income would go to rent. That is a severe rent burden.`;
}

let compareText = "";
if (diff > 0.2) {
compareText = `If you went to <strong>${college}</strong> instead of <strong>University of Minnesota</strong>, your rent burden would jump from <strong>${umnRatio.toFixed(1)}%</strong> to <strong>${yourRatio.toFixed(1)}%</strong>.`;
} else if (diff < -0.2) {
compareText = `Compared with <strong>University of Minnesota</strong>, choosing <strong>${college}</strong> would lower your rent burden from <strong>${umnRatio.toFixed(1)}%</strong> to <strong>${yourRatio.toFixed(1)}%</strong>.`;
} else {
compareText = `<strong>${college}</strong> and <strong>University of Minnesota</strong> would create almost the same rent burden for your income: <strong>${yourRatio.toFixed(1)}%</strong> versus <strong>${umnRatio.toFixed(1)}%</strong>.`;
}

let incomeNeededText = "";
if (incomeGap <= 0) {
incomeNeededText = `At your current income, you already clear the affordability threshold here. To stay under 30%, you would need about <strong>${currency(neededIncome)}</strong>, and you are above that.`;
} else {
incomeNeededText = `To live in <strong>${info.state}</strong> without being cost-burdened, you would need about <strong>${currency(neededIncome)}</strong> per year. That is about <strong>${currency(incomeGap)}</strong> more than your current income.`;
}

let rentShockText = "";
if (shockRatio < 30) {
rentShockText = `If rent rose by 10%, your burden would become <strong>${shockRatio.toFixed(1)}%</strong>. You would still remain under the affordability line.`;
} else if (shockRatio < 50) {
rentShockText = `If rent rose by 10%, your burden would become <strong>${shockRatio.toFixed(1)}%</strong>. That would put more pressure on your budget.`;
} else {
rentShockText = `If rent rose by 10%, your burden would jump to <strong>${shockRatio.toFixed(1)}%</strong>. That would push this option into a very difficult range.`;
}

verdict.innerHTML = verdictText;
details.innerHTML = `
<strong>State:</strong> ${info.state}<br>
<strong>Median annual rent in that state:</strong> ${currency(info.rent)}<br>
<strong>Statewide under-25 burden:</strong> ${info.state_burden.toFixed(1)}%
`;
compare.innerHTML = compareText;
gauge.innerHTML = drawCollegeGauge(yourRatio);
badgeWrap.innerHTML = badgeHTML(yourRatio);
incomeNeededBox.innerHTML = incomeNeededText;
rentShockBox.innerHTML = rentShockText;
results.style.display = "block";
}

function findAffordableAlternatives() {
const income = parseFloat(document.getElementById("go-income").value);
const selectedCollege = document.getElementById("go-college").value;
const altWrap = document.getElementById("go-alt-results");
const altGrid = document.getElementById("go-alt-grid");

if (!income || income <= 0) {
altWrap.style.display = "block";
altGrid.innerHTML = `<div class="go-alt-card">Please enter your income first.</div>`;
return;
}

const matches = Object.entries(COLLEGE_DATA)
.map(([college, info]) => ({
college: college,
state: info.state,
rent: info.rent,
ratio: (info.rent / income) * 100
}))
.filter(d => d.college !== selectedCollege)
.sort((a, b) => a.ratio - b.ratio)
.slice(0, 5);

altWrap.style.display = "block";

altGrid.innerHTML = matches.map(d => `
<div class="go-alt-card">
<div class="go-alt-college">${d.college}</div>
<div class="go-alt-state">${d.state}</div>
<div class="go-alt-metric">
<strong>Personal burden:</strong> ${d.ratio.toFixed(1)}%<br>
<strong>Median annual rent:</strong> ${currency(d.rent)}<br>
<strong>Category:</strong> ${burdenLabel(d.ratio)}
</div>
</div>
`).join("");
}

function recommendStates() {
const income = parseFloat(document.getElementById("go-income").value);
const moveWrap = document.getElementById("go-move-results");
const moveGrid = document.getElementById("go-move-grid");

if (!income || income <= 0) {
moveWrap.style.display = "block";
moveGrid.innerHTML = `<div class="go-alt-card">Enter your income first to see the best states for you.</div>`;
return;
}

const ranked = STATE_DATA
.map(d => ({
state: d.state,
rent: d.rent,
ratio: (d.rent / income) * 100
}))
.sort((a, b) => a.ratio - b.ratio)
.slice(0, 5);

moveWrap.style.display = "block";
moveGrid.innerHTML = ranked.map(d => `
<div class="go-alt-card">
<div class="go-alt-college">${d.state}</div>
<div class="go-alt-metric">
<strong>Your burden:</strong> ${d.ratio.toFixed(1)}%<br>
<strong>Median annual rent:</strong> ${currency(d.rent)}<br>
${movePill(d.ratio)}
</div>
</div>
`).join("");
}
</script>'
))
```



<div class="section-title">All 50 States Ranked</div>
<div class="section-subtitle">Hover any bar for full details. Sorted from most to least burdened.</div>

```{r}
#| label: all-states
#| echo: false
#| message: false
#| warning: false
#| fig-height: 14

COLORS <- c(
  "Affordable"        = "#27ae60",
  "Burdened"          = "#e67e22",
  "Severely Burdened" = "#c0392b"
)

p5 <- ggplot(burden_2023,
  aes(x = fct_reorder(State, burden_under25),
      y = burden_under25,
      fill = burden_cat_under25,
      text = paste0(
        "<b>", State, "</b><br>",
        "Burden: ", round(burden_under25, 1), "%<br>",
        "Category: ", burden_cat_under25, "<br>",
        "Annual Rent: $", format(round(median_rent_annual), big.mark = ","), "<br>",
        "Income (Under 25): $", format(round(income_under25), big.mark = ",")
      ))) +
  geom_col(width = 0.75, alpha = 0.90) +
  geom_hline(yintercept = 30, linetype = "dashed", color = "#1a1a2e", linewidth = 0.7, alpha = 0.6) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "#c0392b", linewidth = 0.7, alpha = 0.6) +
  coord_flip() +
  scale_fill_manual(values = COLORS, name = "Burden Category") +
  scale_y_continuous(labels = label_percent(scale = 1)) +
  labs(x = NULL, y = "Rent Burden Ratio (%)") +
  theme_minimal(base_size = 11) +
  theme(axis.text.y = element_text(size = 8.5), legend.position = "top",
        panel.grid.minor = element_blank())

ggplotly(p5, tooltip = "text", height = 900) %>%
  layout(legend = list(orientation = "h", x = 0, y = 1.02),
         font = list(family = "sans-serif"),
         margin = list(l = 120))
```

```{=html}
<div class="section-title">What This Means</div>
<div class="conclusion-grid">
  <div class="conclusion-card">
    <h4>College Choice Is a Housing Decision</h4>
    <p>States with major university hubs like California, Florida, and New York are among the least affordable for young renters. Students in these states face housing costs that consume nearly half their income.</p>
  </div>
  <div class="conclusion-card">
    <h4>The Income Gap Is the Real Problem</h4>
    <p>Young renters are not paying dramatically higher rents than older adults. They are paying similar rents on dramatically lower incomes. High burden comes from low income, not unusually high rent.</p>
  </div>
  <div class="conclusion-card">
    <h4>Rural States Are Affordable But Less Accessible</h4>
    <p>Wyoming, North Dakota, and Arkansas show the lowest burden ratios. But these states also have fewer universities, fewer entry-level jobs, and fewer opportunities for young graduates.</p>
  </div>
  <div class="conclusion-card">
    <h4>This Gap Will Not Fix Itself</h4>
    <p>The burden gap hits hardest during the years when people are building careers and finishing school. Every under-25 renter today is making decisions whose financial consequences last decades.</p>
  </div>
</div>

<div style="background:#f8f9fa;border-radius:16px;padding:24px;margin:30px 0;font-size:0.85em;color:#666;line-height:1.8;">
  <strong style="color:#1a1a2e;">Data Sources</strong><br>
  Income by Age: U.S. Census Bureau ACS 1-Year Estimates Table B19049 (2015-2023, excluding 2020)<br>
  Median Gross Rent: U.S. Census Bureau ACS 1-Year Estimates Table B25064 (2015-2023, excluding 2020)<br>
  Historical Income: U.S. Census Bureau CPS Historical Income Table H-8 (1984-2024)<br>
  Data via tidycensus R package. Puerto Rico excluded. 2020 ACS not released due to COVID-19.
</div>
```
