---
title: "Rent & Roster"
subtitle: "Can college-age renters actually afford to live in the U.S.?"
author:
  - "Elma M."
  - "Jack D."
  - "Thusa"
date: today
format:
  html:
    page-layout: full
    toc: false
---

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

library(tidycensus)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(plotly)
library(leaflet)
library(tigris)
library(sf)
library(scales)
library(forcats)
library(htmltools)

readRenviron("~/.Renviron")
options(tigris_use_cache = TRUE)
```

```{r}
#| label: load-data
#| echo: false
#| message: false
#| warning: false
#| cache: true

years <- c(2015, 2016, 2017, 2018, 2019, 2021, 2022, 2023)

income_by_age_raw <- map_dfr(years, function(yr) {
  get_acs(
    geography = "state",
    variables = c(
      "under25"  = "B19049_002",
      "age25_44" = "B19049_003"
    ),
    year   = yr,
    survey = "acs1"
  ) %>%
    mutate(year = yr)
})

rent_raw <- map_dfr(years, function(yr) {
  get_acs(
    geography = "state",
    variables = "B25064_001",
    year   = yr,
    survey = "acs1"
  ) %>%
    mutate(year = yr)
})

income_2023 <- income_by_age_raw %>%
  filter(year == 2023) %>%
  select(State = NAME, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate) %>%
  rename(income_under25 = under25, income_25_44 = age25_44)

rent_2023 <- rent_raw %>%
  filter(year == 2023) %>%
  select(State = NAME, median_rent_monthly = estimate) %>%
  mutate(median_rent_annual = median_rent_monthly * 12)

burden_2023 <- income_2023 %>%
  inner_join(rent_2023, by = "State") %>%
  filter(State != "Puerto Rico") %>%
  mutate(
    burden_under25 = (median_rent_annual / income_under25) * 100,
    burden_cat_under25 = case_when(
      burden_under25 < 30  ~ "Affordable",
      burden_under25 < 50  ~ "Burdened",
      burden_under25 >= 50 ~ "Severely Burdened"
    ),
    burden_25_44 = (median_rent_annual / income_25_44) * 100,
    burden_cat_25_44 = case_when(
      burden_25_44 < 30  ~ "Affordable",
      burden_25_44 < 50  ~ "Burdened",
      burden_25_44 >= 50 ~ "Severely Burdened"
    )
  ) %>%
  arrange(desc(burden_under25))
```

```{=html}
<style>
* { box-sizing: border-box; }
.hero {
  background: linear-gradient(135deg, #0f0c29, #302b63, #24243e);
  color: white; padding: 80px 40px; text-align: center;
  margin: -20px -20px 40px -20px; border-radius: 0 0 20px 20px;
  position: relative; overflow: hidden;
}
.hero::before {
  content: ""; position: absolute; top: 0; left: 0; right: 0; bottom: 0;
  background: radial-gradient(ellipse at 30% 50%, rgba(231,76,60,0.15) 0%, transparent 60%),
              radial-gradient(ellipse at 70% 50%, rgba(52,152,219,0.1) 0%, transparent 60%);
}
.hero h1 { font-size: 3.5em; font-weight: 900; margin: 0 0 10px 0; letter-spacing: -1px; position: relative; }
.hero p { font-size: 1.3em; opacity: 0.85; max-width: 600px; margin: 0 auto 30px auto; position: relative; }
.stats-row { display: flex; justify-content: center; gap: 40px; flex-wrap: wrap; margin-top: 40px; position: relative; }
.stat-box {
  background: rgba(255,255,255,0.1); border: 1px solid rgba(255,255,255,0.2);
  border-radius: 16px; padding: 24px 32px; text-align: center; min-width: 160px;
  backdrop-filter: blur(10px);
}
.stat-number { font-size: 3em; font-weight: 900; color: #e74c3c; display: block; line-height: 1; }
.stat-label { font-size: 0.85em; opacity: 0.8; margin-top: 6px; line-height: 1.4; }
.section-title {
  font-size: 2em; font-weight: 800; color: #1a1a2e;
  margin: 60px 0 10px 0; border-left: 5px solid #e74c3c; padding-left: 16px;
}
.section-subtitle { color: #666; font-size: 1.1em; margin-bottom: 24px; padding-left: 21px; }
.intro-block {
  background: linear-gradient(135deg, #f8f9fa, #fff);
  border-radius: 20px; padding: 40px; margin: 30px 0;
  border: 1px solid #e9ecef;
  display: grid; grid-template-columns: 1fr 1fr; gap: 40px;
}
@media(max-width:768px) { .intro-block { grid-template-columns: 1fr; } }
.intro-block h3 { font-size: 1.2em; font-weight: 800; color: #1a1a2e; margin: 0 0 12px 0; }
.intro-block p { color: #555; line-height: 1.75; margin: 0 0 12px 0; font-size: 0.95em; }
.rq-list { list-style: none; padding: 0; margin: 0; }
.rq-list li {
  padding: 12px 16px; margin-bottom: 10px;
  background: white; border-radius: 10px; border-left: 4px solid #e74c3c;
  font-size: 0.92em; color: #333; line-height: 1.5;
  box-shadow: 0 2px 8px rgba(0,0,0,0.06);
}
.rq-num { font-weight: 900; color: #e74c3c; margin-right: 8px; }
.team-row { display: flex; gap: 16px; margin-top: 16px; flex-wrap: wrap; }
.team-card {
  background: white; border-radius: 12px; padding: 16px 20px;
  border-top: 3px solid #e74c3c; flex: 1; min-width: 120px;
  box-shadow: 0 2px 8px rgba(0,0,0,0.06); text-align: center;
}
.team-card .name { font-weight: 800; color: #1a1a2e; font-size: 0.95em; }
.team-card .role { color: #888; font-size: 0.8em; margin-top: 4px; }
.calc-container {
  background: linear-gradient(135deg, #1a1a2e, #16213e);
  border-radius: 20px; padding: 40px; color: white; margin: 20px 0;
}
.calc-title { font-size: 1.5em; font-weight: 800; margin: 0 0 8px 0; }
.calc-subtitle { opacity: 0.7; margin-bottom: 30px; font-size: 0.95em; }
.calc-inputs { display: flex; gap: 16px; flex-wrap: wrap; margin-bottom: 20px; }
.calc-input-group { flex: 1; min-width: 200px; }
.calc-input-group label { display: block; font-size: 0.85em; font-weight: 600; margin-bottom: 8px; opacity: 0.8; text-transform: uppercase; }
.calc-input-group input, .calc-input-group select {
  width: 100%; padding: 14px 16px; border: 2px solid rgba(255,255,255,0.2);
  border-radius: 10px; font-size: 15px;
  background: rgba(255,255,255,0.1); color: white; outline: none;
}
.calc-input-group input::placeholder { color: rgba(255,255,255,0.4); }
.calc-input-group select option { background: #1a1a2e; }
.calc-btn {
  background: #e74c3c; color: white; border: none;
  padding: 14px 36px; border-radius: 10px; font-size: 16px;
  font-weight: 700; cursor: pointer; transition: all 0.2s;
}
.calc-btn:hover { background: #c0392b; transform: translateY(-1px); }
.result-gauge { margin-top: 30px; display: none; }
.result-details { background: rgba(255,255,255,0.08); border-radius: 12px; padding: 20px; margin-top: 16px; }
.result-verdict { font-size: 1.1em; line-height: 1.6; margin-bottom: 12px; }
.result-rent-line { font-size: 0.85em; opacity: 0.6; }
.story-section { padding: 40px 0; border-bottom: 1px solid #eee; max-width: 700px; }
.story-section:last-child { border-bottom: none; }
.big-number { font-size: 5em; font-weight: 900; color: #e74c3c; line-height: 1; margin-bottom: 10px; }
.plots-grid { display: grid; grid-template-columns: 1fr 1fr; gap: 24px; margin: 30px 0; }
@media(max-width:768px) { .plots-grid { grid-template-columns: 1fr; } }
.plot-card {
  background: white; border-radius: 16px; padding: 20px;
  box-shadow: 0 4px 20px rgba(0,0,0,0.08); border: 1px solid #f0f0f0;
}
.plot-card h4 { font-size: 0.9em; font-weight: 700; color: #1a1a2e; margin: 0 0 12px 0; text-transform: uppercase; letter-spacing: 0.05em; }
.plot-card img { width: 100%; border-radius: 8px; }
.plot-card-full { grid-column: 1 / -1; }
.vs-container {
  background: linear-gradient(135deg, #1a1a2e, #2c3e50);
  border-radius: 20px; padding: 40px; color: white; margin: 20px 0;
}
.vs-title { font-size: 1.5em; font-weight: 800; margin: 0 0 8px 0; }
.vs-subtitle { opacity: 0.7; margin-bottom: 28px; font-size: 0.95em; }
.vs-inputs { display: flex; gap: 16px; align-items: flex-end; flex-wrap: wrap; margin-bottom: 20px; }
.vs-input-group { flex: 1; min-width: 180px; }
.vs-input-group label { display: block; font-size: 0.82em; font-weight: 700; margin-bottom: 8px; opacity: 0.75; text-transform: uppercase; letter-spacing: 0.05em; }
.vs-input-group select {
  width: 100%; padding: 13px 16px; border: 2px solid rgba(255,255,255,0.15);
  border-radius: 10px; font-size: 14px;
  background: rgba(255,255,255,0.1); color: white; outline: none;
}
.vs-input-group select option { background: #1a1a2e; color: white; }
.vs-divider { font-size: 1.8em; font-weight: 900; opacity: 0.5; padding-bottom: 8px; }
.vs-btn {
  background: #e74c3c; color: white; border: none;
  padding: 13px 32px; border-radius: 10px; font-size: 15px;
  font-weight: 700; cursor: pointer; transition: all 0.2s; white-space: nowrap;
}
.vs-btn:hover { background: #c0392b; transform: translateY(-1px); }
.vs-result { display: none; margin-top: 28px; }
.vs-cards { display: grid; grid-template-columns: 1fr auto 1fr; gap: 16px; align-items: center; }
@media(max-width:600px) { .vs-cards { grid-template-columns: 1fr; } }
.vs-card {
  background: rgba(255,255,255,0.08); border-radius: 16px; padding: 24px;
  border: 1px solid rgba(255,255,255,0.1); text-align: center;
}
.vs-card.winner { border-color: #27ae60; background: rgba(39,174,96,0.12); }
.vs-card.loser { border-color: rgba(255,255,255,0.1); opacity: 0.85; }
.vs-state-name { font-size: 1.2em; font-weight: 800; margin-bottom: 16px; }
.vs-big-pct { font-size: 3em; font-weight: 900; line-height: 1; margin-bottom: 6px; }
.vs-pct-label { font-size: 0.8em; opacity: 0.65; margin-bottom: 16px; }
.vs-metric { font-size: 0.88em; opacity: 0.75; line-height: 1.8; }
.vs-badge {
  display: inline-block; padding: 6px 14px; border-radius: 20px;
  font-size: 0.8em; font-weight: 700; margin-top: 12px;
}
.vs-middle { text-align: center; }
.vs-vs { font-size: 2em; font-weight: 900; opacity: 0.4; }
.vs-winner-tag { font-size: 0.75em; font-weight: 700; color: #27ae60; margin-top: 8px; }
.vs-verdict {
  margin-top: 20px; background: rgba(255,255,255,0.06);
  border-radius: 12px; padding: 18px 22px; font-size: 0.95em;
  line-height: 1.7; opacity: 0.9;
}
.conclusion-section {
  background: linear-gradient(135deg, #0f0c29, #1a1a2e);
  color: white; border-radius: 20px; padding: 50px 40px; margin: 40px 0;
}
.conclusion-section h2 { font-size: 2em; font-weight: 900; margin: 0 0 8px 0; }
.conclusion-section .sub { opacity: 0.65; margin-bottom: 36px; font-size: 1em; }
.conclusion-grid {
  display: grid; grid-template-columns: repeat(auto-fit, minmax(240px, 1fr));
  gap: 20px; margin-bottom: 36px;
}
.conclusion-card {
  background: rgba(255,255,255,0.07); border-radius: 16px; padding: 24px;
  border-top: 3px solid;
}
.conclusion-card h4 { margin: 0 0 10px 0; color: white; font-size: 0.95em; font-weight: 800; }
.conclusion-card p { margin: 0; color: rgba(255,255,255,0.7); font-size: 0.88em; line-height: 1.65; }
.final-statement {
  background: rgba(231,76,60,0.15); border-radius: 14px; padding: 24px 28px;
  border-left: 4px solid #e74c3c; font-size: 1.05em; line-height: 1.75;
  color: rgba(255,255,255,0.9);
}
</style>

<div class="hero">
  <h1>Can You Afford to Rent?</h1>
  <p>A data investigation into student housing affordability across all 50 U.S. states</p>
  <div class="stats-row">
    <div class="stat-box">
      <span class="stat-number" id="c1">0</span>
      <div class="stat-label">states burden<br>young renters</div>
    </div>
    <div class="stat-box">
      <span class="stat-number" id="c2">0%</span>
      <div class="stat-label">average burden<br>for under-25</div>
    </div>
    <div class="stat-box">
      <span class="stat-number" id="c3">0</span>
      <div class="stat-label">states burden<br>ages 25-44</div>
    </div>
    <div class="stat-box">
      <span class="stat-number" id="c4">0x</span>
      <div class="stat-label">higher burden<br>young vs older</div>
    </div>
  </div>
</div>

<script>
function animCount(id, target, suffix, dur) {
  const el = document.getElementById(id);
  let v = 0;
  const step = target / (dur / 16);
  const t = setInterval(() => {
    v += step;
    if (v >= target) { el.textContent = target + suffix; clearInterval(t); }
    else { el.textContent = Math.floor(v) + suffix; }
  }, 16);
}
window.addEventListener("load", () => {
  setTimeout(() => {
    animCount("c1", 34, "", 1500);
    animCount("c2", 34, "%", 1500);
    animCount("c3", 0, "", 500);
    animCount("c4", 2, "x", 1000);
  }, 400);
});
function getColor(r) {
  if (r < 30) return "#27ae60";
  if (r < 50) return "#e67e22";
  return "#e74c3c";
}
function drawGauge(ratio, containerId) {
  const color = getColor(ratio);
  const angle = Math.min((ratio / 60) * 180, 180);
  const rad = (angle - 180) * Math.PI / 180;
  const x = 100 + 80 * Math.cos(rad);
  const y = 100 + 80 * Math.sin(rad);
  const el = document.getElementById(containerId);
  if (!el) return;
  el.innerHTML = `<svg width="200" height="110" viewBox="0 0 200 110">
    <path d="M 20 100 A 80 80 0 0 1 180 100" fill="none" stroke="#eee" stroke-width="16" stroke-linecap="round"/>
    <path d="M 20 100 A 80 80 0 0 1 180 100" fill="none" stroke="${color}" stroke-width="16"
      stroke-linecap="round" stroke-dasharray="${angle * 80 * Math.PI / 180} 1000"/>
    <line x1="100" y1="100" x2="${x}" y2="${y}" stroke="#1a1a2e" stroke-width="3" stroke-linecap="round"/>
    <circle cx="100" cy="100" r="5" fill="#1a1a2e"/>
    <text x="100" y="72" text-anchor="middle" font-size="22" font-weight="900" fill="${color}">${ratio}%</text>
    <text x="20" y="112" font-size="9" fill="#999">0%</text>
    <text x="88" y="22" font-size="9" fill="#999">30%</text>
    <text x="170" y="112" font-size="9" fill="#999">60%</text>
  </svg>`;
}
</script>

<div class="section-title">About This Project</div>

```{=html}
<div class="intro-block">
  <div>
    <h3>What We Set Out to Answer</h3>
    <p>All three of us are students navigating housing costs right now. When we started this project, we had a simple question: is what we are living through measurable? And is it systematically worse for students and young renters than for everyone else?</p>
    <p>We pulled data from the U.S. Census Bureau American Community Survey covering rent and income by age group across all 51 states. What we found was more alarming than we expected.</p>
    <p>This site is the full story: the data, the visualizations, the interactive tools, and the conclusions.</p>
    <div class="team-row">
      <div class="team-card"><div class="name">Elma M.</div><div class="role">EDA Lead</div></div>
      <div class="team-card"><div class="name">Jack D.</div><div class="role">Income Analysis</div></div>
      <div class="team-card"><div class="name">Thusa</div><div class="role">Team Member</div></div>
    </div>
  </div>
  <div>
    <h3>Our Research Questions</h3>
    <ul class="rq-list">
      <li><span class="rq-num">01</span>Which states are most and least affordable for college-age renters aged 18 to 24, and how does that compare to older adults aged 25 to 44?</li>
      <li><span class="rq-num">02</span>What is the rent-to-income burden ratio for under-25 householders by state, and how many fall into burdened or severely burdened categories?</li>
      <li><span class="rq-num">03</span>How has the affordability gap between younger renters and established adults changed over time, and which states show the biggest generational disparities?</li>
    </ul>
    <p style="margin-top:16px;font-size:0.85em;color:#888;">Data: ACS 1-Year Estimates B19049 + B25064, 2015-2023 (excl. 2020). Census H-8 Historical Income Tables. Via tidycensus R package.</p>
  </div>
</div>
```

<div class="section-title">The Map: Rent Burden and Universities</div>
<div class="section-subtitle">States colored by rent burden for under-25 renters. Click any graduation cap pin to see how affordable that state is for students.</div>

```{r}
#| label: university-map
#| echo: false
#| message: false
#| warning: false

universities <- data.frame(
  name = c(
    "UCLA", "UC Berkeley", "Stanford University", "USC",
    "University of Miami", "Florida State University", "University of Florida",
    "NYU", "Columbia University", "Cornell University",
    "University of Texas Austin", "Texas A&M", "Rice University",
    "University of Michigan", "Michigan State University",
    "University of Washington", "University of Colorado Boulder",
    "Arizona State University", "University of Arizona",
    "Georgia Tech", "University of Georgia",
    "University of Maryland", "Georgetown University",
    "University of Hawaii Manoa",
    "Indiana University", "Purdue University",
    "University of Minnesota", "University of Wisconsin Madison",
    "Iowa State University", "University of Iowa",
    "University of Oregon", "Oregon State University",
    "Penn State University", "University of Pennsylvania",
    "University of North Carolina", "NC State University",
    "Louisiana State University", "Tulane University",
    "University of Alabama", "Auburn University",
    "University of Kentucky", "University of Louisville",
    "West Virginia University", "University of Virginia",
    "University of Nevada Las Vegas", "University of New Mexico",
    "University of Montana", "University of Wyoming",
    "University of Vermont", "University of Rhode Island",
    "University of Connecticut", "University of South Carolina",
    "Clemson University", "University of Tennessee",
    "Vanderbilt University", "University of Arkansas",
    "University of Oklahoma", "Oklahoma State University",
    "University of Nebraska Lincoln",
    "University of North Dakota", "North Dakota State University",
    "Kansas State University", "University of Kansas",
    "University of Mississippi", "Mississippi State University",
    "University of Delaware",
    "University of South Dakota", "South Dakota State University",
    "University of Maine", "University of Idaho",
    "University of Alaska Fairbanks",
    "Macalester College", "Harvard University", "MIT",
    "Boston University", "Yale University", "Princeton University",
    "University of Chicago", "Carnegie Mellon University",
    "Ohio State University", "Northwestern University",
    "Emory University", "University of Central Florida"
  ),
  lat = c(
    34.0689, 37.8724, 37.4275, 34.0224,
    25.7142, 30.4420, 29.6465,
    40.7295, 40.8075, 42.4534,
    30.2849, 30.6187, 29.7174,
    42.2780, 42.7009,
    47.6553, 40.0076,
    33.4255, 32.2319,
    33.7756, 33.9480,
    38.9869, 38.9076,
    21.2969,
    39.1682, 40.4259,
    44.9740, 43.0753,
    42.0140, 41.6611,
    44.0460, 44.5646,
    40.7982, 39.9526,
    35.9049, 35.7847,
    30.4133, 29.9384,
    33.2148, 32.6099,
    38.0473, 38.2527,
    39.6350, 38.0336,
    36.1140, 35.0844,
    46.8625, 42.8666,
    44.4759, 41.4801,
    41.8084, 33.9979,
    34.6834, 35.9546,
    36.1447, 36.0671,
    35.2076, 36.1156,
    40.8202,
    47.9219, 46.8974,
    39.1836, 38.9543,
    34.3648, 33.4554,
    39.6784,
    43.0760, 44.3168,
    44.9015, 46.7196,
    64.8581,
    44.9375, 42.3770, 42.3601,
    42.3505, 41.3163, 40.3430,
    41.7886, 40.4444,
    40.0076, 42.0565,
    33.7925, 28.6024
  ),
  lng = c(
    -118.4452, -122.2595, -122.1697, -118.2851,
    -80.2790, -84.2980, -82.3520,
    -73.9965, -73.9626, -76.4735,
    -97.7341, -96.3365, -95.4019,
    -83.7382, -84.4821,
    -122.3035, -105.2659,
    -111.9400, -110.9501,
    -84.3963, -83.3776,
    -76.9426, -77.0735,
    -157.8167,
    -86.5230, -86.9081,
    -93.2350, -89.4012,
    -93.6465, -91.5550,
    -123.0694, -123.2780,
    -77.8600, -75.1932,
    -79.0469, -78.6785,
    -91.1800, -90.1183,
    -87.5450, -85.4808,
    -84.5047, -85.7585,
    -79.9559, -78.5080,
    -115.1398, -106.6504,
    -114.0120, -108.9658,
    -73.1937, -71.5274,
    -72.2495, -81.0219,
    -82.8374, -83.9274,
    -86.8025, -94.1792,
    -97.4395, -96.5925,
    -96.7005,
    -101.9971, -96.7833,
    -96.5717, -95.2483,
    -89.5377, -88.7873,
    -75.7497,
    -96.9040, -96.8022,
    -68.9675, -116.9190,
    -147.8469,
    -93.1710, -71.1167, -71.0942,
    -71.1054, -72.9223, -74.6514,
    -87.5987, -79.9532,
    -83.0300, -87.6753,
    -84.3267, -81.2001
  ),
  state = c(
    "California", "California", "California", "California",
    "Florida", "Florida", "Florida",
    "New York", "New York", "New York",
    "Texas", "Texas", "Texas",
    "Michigan", "Michigan",
    "Washington", "Colorado",
    "Arizona", "Arizona",
    "Georgia", "Georgia",
    "Maryland", "District of Columbia",
    "Hawaii",
    "Indiana", "Indiana",
    "Minnesota", "Wisconsin",
    "Iowa", "Iowa",
    "Oregon", "Oregon",
    "Pennsylvania", "Pennsylvania",
    "North Carolina", "North Carolina",
    "Louisiana", "Louisiana",
    "Alabama", "Alabama",
    "Kentucky", "Kentucky",
    "West Virginia", "Virginia",
    "Nevada", "New Mexico",
    "Montana", "Wyoming",
    "Vermont", "Rhode Island",
    "Connecticut", "South Carolina",
    "South Carolina", "Tennessee",
    "Tennessee", "Arkansas",
    "Oklahoma", "Oklahoma",
    "Nebraska",
    "North Dakota", "North Dakota",
    "Kansas", "Kansas",
    "Mississippi", "Mississippi",
    "Delaware",
    "South Dakota", "South Dakota",
    "Maine", "Idaho",
    "Alaska",
    "Minnesota", "Massachusetts", "Massachusetts",
    "Massachusetts", "Connecticut", "New Jersey",
    "Illinois", "Pennsylvania",
    "Ohio", "Illinois",
    "Georgia", "Florida"
  )
) %>%
  left_join(
    burden_2023 %>% select(State, burden_under25, burden_cat_under25,
                           median_rent_annual, income_under25),
    by = c("state" = "State")
  ) %>%
  mutate(
    bg_color = case_when(
      burden_under25 < 30 ~ "#d4edda",
      burden_under25 < 50 ~ "#fff3cd",
      TRUE                ~ "#f8d7da"
    ),
    txt_color = case_when(
      burden_under25 < 30 ~ "#155724",
      burden_under25 < 50 ~ "#856404",
      TRUE                ~ "#721c24"
    ),
    popup_text = paste0(
      "<div style='font-family:sans-serif;min-width:240px;padding:4px;'>",
      "<div style='font-size:1.1em;font-weight:800;color:#1a1a2e;margin-bottom:4px;'>", name, "</div>",
      "<div style='font-size:0.82em;color:#888;margin-bottom:10px;'>", state, "</div>",
      "<div style='background:", bg_color, ";padding:12px;border-radius:10px;margin-bottom:10px;text-align:center;'>",
      "<div style='font-size:2em;font-weight:900;color:", txt_color, ";'>", round(burden_under25, 1), "%</div>",
      "<div style='font-size:0.78em;color:", txt_color, ";'>rent burden for under-25 renters</div>",
      "</div>",
      "<div style='font-size:0.85em;line-height:1.8;'>",
      "<b>Annual Rent:</b> $", format(round(median_rent_annual), big.mark = ","), "<br>",
      "<b>Under-25 Income:</b> $", format(round(income_under25), big.mark = ","), "<br>",
      "<b>Category:</b> <span style='font-weight:700;color:", txt_color, ";'>", burden_cat_under25, "</span>",
      "</div></div>"
    ),
    marker_color = case_when(
      burden_under25 < 30 ~ "green",
      burden_under25 < 50 ~ "orange",
      TRUE                ~ "red"
    )
  )

states_sf2 <- tigris::states(cb = TRUE, resolution = "20m", year = 2022) %>%
  filter(!STUSPS %in% c("PR", "GU", "VI", "MP", "AS")) %>%
  sf::st_transform(crs = 4326) %>%
  left_join(burden_2023, by = c("NAME" = "State"))

pal2 <- colorNumeric(palette = c("#27ae60", "#f39c12", "#e74c3c"), domain = c(10, 55))

icon_green  <- makeAwesomeIcon(icon = "graduation-cap", library = "fa", markerColor = "green",  iconColor = "white")
icon_orange <- makeAwesomeIcon(icon = "graduation-cap", library = "fa", markerColor = "orange", iconColor = "white")
icon_red    <- makeAwesomeIcon(icon = "graduation-cap", library = "fa", markerColor = "red",    iconColor = "white")

unis_g <- universities %>% filter(marker_color == "green")
unis_o <- universities %>% filter(marker_color == "orange")
unis_r <- universities %>% filter(marker_color == "red")

m <- leaflet(states_sf2) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(
    fillColor = ~pal2(burden_under25), fillOpacity = 0.65,
    color = "white", weight = 1, smoothFactor = 0.5,
    label = ~paste0(NAME, ": ", round(burden_under25, 1), "% burden") %>% lapply(htmltools::HTML),
    labelOptions = labelOptions(style = list("font-weight" = "bold", padding = "4px 8px"), textsize = "12px")
  ) %>%
  addLegend(pal = pal2, values = ~burden_under25,
    title = "Rent Burden (%)<br><small>Under-25 Householders</small>",
    position = "bottomleft", labFormat = labelFormat(suffix = "%"))

if (nrow(unis_g) > 0) m <- m %>% addAwesomeMarkers(data = unis_g, lng = ~lng, lat = ~lat, icon = icon_green, popup = ~popup_text, label = ~name, group = "Affordable States")
if (nrow(unis_o) > 0) m <- m %>% addAwesomeMarkers(data = unis_o, lng = ~lng, lat = ~lat, icon = icon_orange, popup = ~popup_text, label = ~name, group = "Burdened States")
if (nrow(unis_r) > 0) m <- m %>% addAwesomeMarkers(data = unis_r, lng = ~lng, lat = ~lat, icon = icon_red, popup = ~popup_text, label = ~name, group = "Severely Burdened States")

m %>%
  addLayersControl(overlayGroups = c("Affordable States", "Burdened States", "Severely Burdened States"),
    options = layersControlOptions(collapsed = FALSE)) %>%
  setView(lng = -96, lat = 38, zoom = 4)
```

<div class="section-title">The EDA: What the Data Showed</div>
<div class="section-subtitle">Six visualizations from our exploratory data analysis. Every chart tells part of the same story.</div>

```{r}
#| label: eda-plots
#| echo: false
#| message: false
#| warning: false

library(ggrepel)

COLORS_EDA <- c(
  "Affordable (<30%)"        = "#27ae60",
  "Burdened (30-50%)"        = "#e67e22",
  "Severely Burdened (>50%)" = "#c0392b"
)

theme_rb <- function() {
  theme_minimal(base_size = 12) +
    theme(
      plot.title    = element_text(face = "bold", size = 14, color = "#1a1a2e", margin = margin(b = 4)),
      plot.subtitle = element_text(size = 10, color = "#555577", margin = margin(b = 12)),
      plot.caption  = element_text(size = 8, color = "#888899", hjust = 0, margin = margin(t = 8)),
      panel.grid.minor = element_blank(),
      legend.position  = "top",
      plot.background  = element_rect(fill = "#fafafa", color = NA),
      panel.background = element_rect(fill = "#fafafa", color = NA),
      plot.margin = margin(16, 20, 12, 16)
    )
}

burden_2023_eda <- burden_2023 %>%
  mutate(burden_cat_under25 = case_when(
    burden_under25 < 30  ~ "Affordable (<30%)",
    burden_under25 < 50  ~ "Burdened (30-50%)",
    burden_under25 >= 50 ~ "Severely Burdened (>50%)"
  ))

# Plot 1: Distribution
p1 <- ggplot(burden_2023_eda, aes(x = burden_under25, fill = burden_cat_under25)) +
  geom_histogram(bins = 18, color = "white", linewidth = 0.4, alpha = 0.92) +
  geom_vline(xintercept = 30, linetype = "dashed", color = "#1a1a2e", linewidth = 0.8) +
  geom_vline(xintercept = 50, linetype = "dashed", color = "#1a1a2e", linewidth = 0.8) +
  annotate("text", x = 31, y = 8, label = "30% threshold", hjust = 0, size = 3, color = "#1a1a2e", fontface = "italic") +
  scale_fill_manual(values = COLORS_EDA, name = NULL) +
  scale_x_continuous(labels = label_percent(scale = 1)) +
  labs(title = "How Burdened Are Young Renters?",
       subtitle = "Distribution of burden ratios for under-25 householders (2023)",
       x = "Rent Burden Ratio", y = "Number of States",
       caption = "ACS B19049 + B25064, 2023") +
  theme_rb()

# Plot 2: Least affordable
p2 <- burden_2023_eda %>% slice_head(n = 10) %>%
  ggplot(aes(x = fct_reorder(State, burden_under25), y = burden_under25, fill = burden_cat_under25)) +
  geom_col(width = 0.7, alpha = 0.92) +
  geom_text(aes(label = paste0(round(burden_under25, 1), "%")), hjust = -0.15, size = 3, fontface = "bold", color = "#1a1a2e") +
  coord_flip(clip = "off") +
  scale_fill_manual(values = COLORS_EDA, name = NULL) +
  scale_y_continuous(limits = c(0, 58), labels = label_percent(scale = 1)) +
  labs(title = "Top 10 Least Affordable States", subtitle = "Highest rent burden for under-25 (2023)", x = NULL, y = "Burden Ratio (%)") +
  theme_rb() + theme(legend.position = "none")

# Plot 3: Most affordable
p3 <- burden_2023_eda %>% slice_tail(n = 10) %>%
  ggplot(aes(x = fct_reorder(State, burden_under25), y = burden_under25, fill = burden_cat_under25)) +
  geom_col(width = 0.7, alpha = 0.92) +
  geom_text(aes(label = paste0(round(burden_under25, 1), "%")), hjust = -0.15, size = 3, fontface = "bold", color = "#1a1a2e") +
  coord_flip(clip = "off") +
  scale_fill_manual(values = COLORS_EDA, name = NULL) +
  scale_y_continuous(limits = c(0, 35), labels = label_percent(scale = 1)) +
  labs(title = "Top 10 Most Affordable States", subtitle = "Lowest rent burden for under-25 (2023)", x = NULL, y = "Burden Ratio (%)") +
  theme_rb() + theme(legend.position = "none")

# Plot 6: Scatter
p6 <- ggplot(burden_2023_eda,
    aes(x = income_under25, y = median_rent_annual, color = burden_cat_under25, label = State)) +
  geom_abline(slope = 0.30, intercept = 0, linetype = "dashed", color = "#27ae60", linewidth = 0.8) +
  geom_abline(slope = 0.50, intercept = 0, linetype = "dashed", color = "#c0392b", linewidth = 0.8) +
  geom_point(size = 3, alpha = 0.85) +
  geom_text_repel(data = burden_2023_eda %>% filter(burden_under25 > 40 | burden_under25 < 26),
    size = 2.8, color = "#333355", max.overlaps = 15, segment.color = "#ccccdd") +
  scale_color_manual(values = COLORS_EDA, name = NULL) +
  scale_x_continuous(labels = label_dollar()) +
  scale_y_continuous(labels = label_dollar()) +
  annotate("text", x = 58000, y = 58000 * 0.30 + 500, label = "30% burden line", size = 2.8, color = "#27ae60", angle = 18, fontface = "italic") +
  annotate("text", x = 43000, y = 43000 * 0.50 + 500, label = "50% burden line", size = 2.8, color = "#c0392b", angle = 28, fontface = "italic") +
  labs(title = "Income vs. Rent: What Drives Burden?",
       subtitle = "Each dot = one state. Above dashed lines = cost-burdened.",
       x = "Median Annual Income (Under-25)", y = "Median Annual Rent",
       caption = "ACS B19049 + B25064, 2023") +
  theme_rb()
```

```{=html}
<div class="plots-grid">
  <div class="plot-card">
    <h4>Burden Distribution</h4>
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
print(p1)
```

```{=html}
  </div>
  <div class="plot-card">
    <h4>Income vs. Rent</h4>
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
print(p6)
```

```{=html}
  </div>
  <div class="plot-card">
    <h4>Top 10 Least Affordable</h4>
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
print(p2)
```

```{=html}
  </div>
  <div class="plot-card">
    <h4>Top 10 Most Affordable</h4>
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
print(p3)
```

```{=html}
  </div>
</div>
```

<div class="section-title">The Generational Gap</div>
<div class="section-subtitle">Every established adult is affordable. Two thirds of young renters are not.</div>

```{r}
#| label: gen-gap
#| echo: false
#| message: false
#| warning: false

burden_long <- burden_2023 %>%
  select(State, burden_under25, burden_25_44) %>%
  pivot_longer(c(burden_under25, burden_25_44), names_to = "age_group", values_to = "burden_ratio") %>%
  mutate(age_group = recode(age_group,
    "burden_under25" = "Under 25 (college-age)",
    "burden_25_44"   = "Ages 25-44 (established adults)"
  ))

p4 <- ggplot(burden_long,
  aes(x = burden_ratio, fill = age_group,
      text = paste0(age_group, "<br>Burden: ", round(burden_ratio, 1), "%"))) +
  geom_histogram(bins = 20, color = "white", linewidth = 0.3, alpha = 0.82, position = "identity") +
  geom_vline(xintercept = 30, linetype = "dashed", color = "#1a1a2e", linewidth = 1) +
  geom_vline(xintercept = 50, linetype = "dashed", color = "#c0392b", linewidth = 1) +
  annotate("rect", xmin = 30, xmax = 50, ymin = 0, ymax = Inf, alpha = 0.05, fill = "#e67e22") +
  annotate("rect", xmin = 50, xmax = Inf, ymin = 0, ymax = Inf, alpha = 0.08, fill = "#c0392b") +
  annotate("text", x = 31, y = 16, label = "Burdened zone", hjust = 0, size = 3.2, color = "#e67e22", fontface = "italic") +
  annotate("text", x = 51, y = 16, label = "Severely burdened", hjust = 0, size = 3.2, color = "#c0392b", fontface = "italic") +
  scale_fill_manual(values = c("Under 25 (college-age)" = "#e74c3c", "Ages 25-44 (established adults)" = "#3498db"), name = "Age Group") +
  scale_x_continuous(labels = label_percent(scale = 1)) +
  labs(x = "Rent Burden Ratio", y = "Number of States", caption = "ACS 1-Year Estimates (B19049, B25064), 2023") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "top", panel.grid.minor = element_blank())

ggplotly(p4, tooltip = "text") %>%
  layout(legend = list(orientation = "h", x = 0.05, y = 1.12), font = list(family = "sans-serif"))
```

```{=html}
<div class="story-section">
  <div class="big-number">34</div>
  <p style="font-size:1.2em;color:#333;line-height:1.7;">Out of 51 states, <strong>34 place young renters in the cost-burdened category</strong>. In two thirds of the country, a typical under-25 householder spends more than 30 cents of every dollar on rent alone.</p>
</div>
<div class="story-section">
  <div class="big-number">0</div>
  <p style="font-size:1.2em;color:#333;line-height:1.7;">The number of states where adults aged 25-44 are cost-burdened. <strong>Not a single one.</strong> The same rents that crush young budgets are entirely manageable once income catches up.</p>
</div>
<div class="story-section">
  <div class="big-number">2x</div>
  <p style="font-size:1.2em;color:#333;line-height:1.7;">Young renters spend roughly <strong>twice as much of their income on rent</strong> as established adults. Average 33.7% for under-25 versus 17.8% for 25-44. Same apartments. Very different realities.</p>
</div>
```

<div class="section-title">Your Personal Calculator</div>
<div class="section-subtitle">Find out exactly where you stand based on your actual income.</div>

```{r}
#| label: calculator
#| echo: false
#| results: asis

rent_json <- paste0(
  "{",
  paste0('"', burden_2023$State, '":', round(burden_2023$median_rent_annual, 0), collapse = ","),
  "}"
)

cat(paste0('
<div class="calc-container">
  <div class="calc-title">Student Housing Affordability Calculator</div>
  <div class="calc-subtitle">Enter your annual income and pick a state to see your personal rent burden</div>
  <div class="calc-inputs">
    <div class="calc-input-group">
      <label>Your Annual Income ($)</label>
      <input type="number" id="ci" placeholder="e.g. 28000"/>
    </div>
    <div class="calc-input-group">
      <label>Select a State</label>
      <select id="cs"><option value="">Choose a state...</option></select>
    </div>
  </div>
  <button class="calc-btn" onclick="runCalc()">Calculate My Burden</button>
  <div class="result-gauge" id="rg">
    <div style="text-align:center"><div id="cg"></div></div>
    <div class="result-details">
      <div class="result-verdict" id="rv"></div>
      <div class="result-rent-line" id="rl"></div>
    </div>
  </div>
</div>
<script>
const CRD = ', rent_json, ';
const csel = document.getElementById("cs");
Object.keys(CRD).sort().forEach(s => {
  const o = document.createElement("option");
  o.value = s; o.textContent = s; csel.appendChild(o);
});
function runCalc() {
  const income = parseFloat(document.getElementById("ci").value);
  const state  = document.getElementById("cs").value;
  const gDiv   = document.getElementById("rg");
  if (!income || income <= 0 || !state) {
    gDiv.style.display = "block";
    document.getElementById("rv").innerHTML = "<span style=\'color:#f39c12\'>Please enter income and select a state.</span>";
    document.getElementById("rl").textContent = "";
    document.getElementById("cg").innerHTML = "";
    return;
  }
  const rent  = CRD[state];
  const ratio = parseFloat(((rent / income) * 100).toFixed(1));
  gDiv.style.display = "block";
  let verdict;
  if (ratio < 30) {
    verdict = "At <strong>" + ratio + "%</strong> of your income on rent in " + state + ", you fall below the 30% threshold. You have room to save and breathe.";
  } else if (ratio < 50) {
    verdict = "In " + state + ", <strong>" + ratio + "%</strong> of your income goes to rent. That leaves less than 70 cents of every dollar for everything else.";
  } else {
    verdict = "In " + state + ", a staggering <strong>" + ratio + "%</strong> of your income would go to rent. This is a crisis-level burden by every economic standard.";
  }
  document.getElementById("rv").innerHTML = verdict;
  document.getElementById("rl").textContent = "Based on median annual rent of $" + rent.toLocaleString() + " in " + state + " (ACS 2023)";
  drawGauge(ratio, "cg");
}
</script>
'))
```

<div class="section-title">Should I Go There?</div>
<div class="section-subtitle">Enter your income, pick a college, and find out if you can actually afford to live there. We will also find you cheaper alternatives.</div>

```{r}
#| label: college-finder-data
#| echo: false
#| results: asis

uni_data <- universities %>%
  select(name, state, burden_under25, median_rent_annual, income_under25, burden_cat_under25) %>%
  arrange(name)

uni_json <- paste0(
  "{",
  paste0(
    '"', gsub('"', '\\\\"', uni_data$name), '":{"state":"', uni_data$state,
    '","burden":', round(uni_data$burden_under25, 1),
    ',"rent":', round(uni_data$median_rent_annual, 0),
    ',"cat":"', uni_data$burden_cat_under25, '"',
    '}',
    collapse = ","
  ),
  "}"
)

cat('<script>const UD =', uni_json, ';</script>')
```

```{=html}
<div style="background:linear-gradient(135deg,#0f2027,#203a43,#2c5364);border-radius:20px;padding:40px;color:white;margin:20px 0;">
  <div style="font-size:1.5em;font-weight:800;margin:0 0 8px 0;">Should I Go There?</div>
  <div style="opacity:0.7;margin-bottom:28px;font-size:0.95em;">Enter your income and pick a college to see if you can afford to live nearby. We will show you affordable alternatives too.</div>
  <div style="display:flex;gap:16px;flex-wrap:wrap;margin-bottom:20px;">
    <div style="flex:1;min-width:200px;">
      <label style="display:block;font-size:0.85em;font-weight:600;margin-bottom:8px;opacity:0.8;text-transform:uppercase;">Your Annual Income ($)</label>
      <input type="number" id="fi" placeholder="e.g. 28000" style="width:100%;padding:14px 16px;border:2px solid rgba(255,255,255,0.2);border-radius:10px;font-size:15px;box-sizing:border-box;background:rgba(255,255,255,0.1);color:white;outline:none;"/>
    </div>
    <div style="flex:1;min-width:200px;">
      <label style="display:block;font-size:0.85em;font-weight:600;margin-bottom:8px;opacity:0.8;text-transform:uppercase;">Select a University</label>
      <select id="fu" style="width:100%;padding:14px 16px;border:2px solid rgba(255,255,255,0.2);border-radius:10px;font-size:15px;box-sizing:border-box;background:rgba(255,255,255,0.15);color:white;outline:none;">
        <option value="">Choose a university...</option>
      </select>
    </div>
  </div>
  <button onclick="runFinder()" style="background:#e74c3c;color:white;border:none;padding:14px 36px;border-radius:10px;font-size:16px;font-weight:700;cursor:pointer;">Check Affordability</button>
  <div id="finder-result" style="margin-top:28px;display:none;"></div>
</div>

<script>
document.addEventListener("DOMContentLoaded", function() {
  const fuSel = document.getElementById("fu");
  Object.keys(UD).sort().forEach(u => {
    const o = document.createElement("option");
    o.value = u; o.textContent = u + " (" + UD[u].state + ")";
    fuSel.appendChild(o);
  });
});
function runFinder() {
  const income = parseFloat(document.getElementById("fi").value);
  const uni    = document.getElementById("fu").value;
  const res    = document.getElementById("finder-result");
  if (!income || income <= 0 || !uni) {
    res.style.display = "block";
    res.innerHTML = "<span style='color:#f39c12'>Please enter your income and select a university.</span>";
    return;
  }
  const d     = UD[uni];
  const ratio = parseFloat(((d.rent / income) * 100).toFixed(1));
  const color = ratio < 30 ? "#27ae60" : ratio < 50 ? "#e67e22" : "#e74c3c";
  const bg    = ratio < 30 ? "rgba(39,174,96,0.15)" : ratio < 50 ? "rgba(230,126,34,0.15)" : "rgba(231,76,60,0.15)";
  let verdict;
  if (ratio < 30) verdict = "You can afford to live near <strong>" + uni + "</strong>. At " + ratio + "% of your income on rent in " + d.state + ", you are below the affordability threshold.";
  else if (ratio < 50) verdict = "Living near <strong>" + uni + "</strong> would be a stretch. In " + d.state + ", " + ratio + "% of your income would go to rent.";
  else verdict = "Living near <strong>" + uni + "</strong> is financially unsustainable on your income. In " + d.state + ", " + ratio + "% would go to rent alone.";
  const alts = Object.entries(UD)
    .filter(([name, data]) => (data.rent / income) * 100 < 30 && name !== uni)
    .map(([name, data]) => ({ name, state: data.state, ratio: parseFloat(((data.rent / income) * 100).toFixed(1)) }))
    .sort((a, b) => a.ratio - b.ratio).slice(0, 5);
  let altHTML = "";
  if (ratio >= 30 && alts.length > 0) {
    altHTML = "<div style='margin-top:20px;padding-top:20px;border-top:1px solid rgba(255,255,255,0.1);'><div style='font-size:0.9em;font-weight:700;margin-bottom:12px;opacity:0.8;'>Affordable universities on your income:</div>"
      + alts.map(a => "<div style='display:flex;justify-content:space-between;align-items:center;padding:10px 14px;background:rgba(39,174,96,0.12);border-radius:8px;margin-bottom:6px;font-size:0.9em;'><span><strong>" + a.name + "</strong> <span style='opacity:0.6;'>(" + a.state + ")</span></span><span style='color:#27ae60;font-weight:800;'>" + a.ratio + "%</span></div>").join("") + "</div>";
  } else if (ratio < 30) {
    altHTML = "<div style='margin-top:12px;opacity:0.7;font-size:0.9em;'>You are in great shape. Your income works in this state.</div>";
  } else {
    altHTML = "<div style='margin-top:12px;opacity:0.6;font-size:0.9em;'>No universities in our list fall below 30% on your income. Consider states with lower rents like Wyoming or North Dakota.</div>";
  }
  res.style.display = "block";
  res.innerHTML = "<div style='background:" + bg + ";border-radius:12px;padding:24px;'><div style='font-size:2.2em;font-weight:900;color:" + color + ";margin-bottom:8px;'>" + ratio + "% rent burden</div><div style='line-height:1.7;margin-bottom:10px;'>" + verdict + "</div><div style='font-size:0.82em;opacity:0.55;'>Based on median annual rent of $" + d.rent.toLocaleString() + " in " + d.state + " (ACS 2023)</div>" + altHTML + "</div>";
}
</script>
```

<div class="section-title">State vs State</div>
<div class="section-subtitle">Pick any two states and see a head to head breakdown of rent burden, income, and rent.</div>

```{r}
#| label: vs-data
#| echo: false
#| results: asis

vs_json <- paste0(
  "{",
  paste0(
    '"', burden_2023$State, '":{',
    '"rent":', round(burden_2023$median_rent_annual, 0), ',',
    '"income":', round(burden_2023$income_under25, 0), ',',
    '"burden":', round(burden_2023$burden_under25, 1), ',',
    '"cat":"', burden_2023$burden_cat_under25, '"',
    '}',
    collapse = ","
  ),
  "}"
)

cat('<script>const VSD =', vs_json, ';</script>')
```

```{=html}
<div class="vs-container">
  <div class="vs-title">State vs State Battle</div>
  <div class="vs-subtitle">Which state is actually better for a young renter on your income?</div>
  <div class="vs-inputs">
    <div class="vs-input-group">
      <label>State A</label>
      <select id="vsa"><option value="">Choose state A...</option></select>
    </div>
    <div class="vs-divider">vs</div>
    <div class="vs-input-group">
      <label>State B</label>
      <select id="vsb"><option value="">Choose state B...</option></select>
    </div>
    <button class="vs-btn" onclick="runVS()">Compare</button>
  </div>
  <div class="vs-result" id="vs-result">
    <div class="vs-cards">
      <div class="vs-card" id="vs-card-a"></div>
      <div class="vs-middle"><div class="vs-vs">vs</div><div class="vs-winner-tag" id="vs-winner-tag"></div></div>
      <div class="vs-card" id="vs-card-b"></div>
    </div>
    <div class="vs-verdict" id="vs-verdict"></div>
  </div>
</div>

<script>
document.addEventListener("DOMContentLoaded", function() {
  const vsaSel = document.getElementById("vsa");
  const vsbSel = document.getElementById("vsb");
  Object.keys(VSD).sort().forEach(s => {
    [vsaSel, vsbSel].forEach(sel => {
      const o = document.createElement("option");
      o.value = s; o.textContent = s; sel.appendChild(o);
    });
  });
});

function vsColor(b) { return b < 30 ? "#27ae60" : b < 50 ? "#e67e22" : "#e74c3c"; }
function vsBadgeBg(b) { return b < 30 ? "rgba(39,174,96,0.2)" : b < 50 ? "rgba(230,126,34,0.2)" : "rgba(231,76,60,0.2)"; }

function runVS() {
  const sa = document.getElementById("vsa").value;
  const sb = document.getElementById("vsb").value;
  const res = document.getElementById("vs-result");
  if (!sa || !sb || sa === sb) {
    res.style.display = "block";
    document.getElementById("vs-card-a").innerHTML = "<div style='color:#f39c12;'>Please select two different states.</div>";
    document.getElementById("vs-card-b").innerHTML = "";
    document.getElementById("vs-verdict").innerHTML = "";
    document.getElementById("vs-winner-tag").textContent = "";
    return;
  }
  const a = VSD[sa];
  const b = VSD[sb];
  const aWins = a.burden < b.burden;
  const colA = vsColor(a.burden);
  const colB = vsColor(b.burden);

  function cardHTML(state, d, wins) {
    return "<div class='vs-state-name'>" + state + "</div>"
      + "<div class='vs-big-pct' style='color:" + vsColor(d.burden) + ";'>" + d.burden + "%</div>"
      + "<div class='vs-pct-label'>rent burden for under-25</div>"
      + "<div class='vs-metric'>"
      + "<strong>Annual Rent:</strong> $" + d.rent.toLocaleString() + "<br>"
      + "<strong>Under-25 Income:</strong> $" + d.income.toLocaleString() + "<br>"
      + "<strong>Category:</strong> " + d.cat
      + "</div>"
      + "<div class='vs-badge' style='background:" + vsBadgeBg(d.burden) + ";color:" + vsColor(d.burden) + ";'>" + d.cat + "</div>";
  }

  document.getElementById("vs-card-a").className = "vs-card " + (aWins ? "winner" : "loser");
  document.getElementById("vs-card-b").className = "vs-card " + (!aWins ? "winner" : "loser");
  document.getElementById("vs-card-a").innerHTML = cardHTML(sa, a, aWins);
  document.getElementById("vs-card-b").innerHTML = cardHTML(sb, b, !aWins);
  document.getElementById("vs-winner-tag").textContent = (aWins ? sa : sb) + " wins";

  const winner = aWins ? sa : sb;
  const loser  = aWins ? sb : sa;
  const wd = aWins ? a : b;
  const ld = aWins ? b : a;
  const diff = Math.abs(a.burden - b.burden).toFixed(1);

  document.getElementById("vs-verdict").innerHTML =
    "<strong>" + winner + "</strong> is the more affordable state for young renters, with a " + wd.burden + "% burden compared to " + ld.burden + "% in <strong>" + loser + "</strong>. "
    + "That is a difference of " + diff + " percentage points. "
    + "Annual rent in " + winner + " is $" + wd.rent.toLocaleString() + " versus $" + ld.rent.toLocaleString() + " in " + loser + ".";

  res.style.display = "block";
}
</script>
```

<div class="section-title">All 51 States Ranked</div>
<div class="section-subtitle">Hover any bar for full details. Sorted from most to least burdened.</div>

```{r}
#| label: all-states
#| echo: false
#| message: false
#| warning: false
#| fig-height: 14

COLORS <- c("Affordable" = "#27ae60", "Burdened" = "#e67e22", "Severely Burdened" = "#c0392b")

p5 <- ggplot(burden_2023,
  aes(x = fct_reorder(State, burden_under25), y = burden_under25,
      fill = burden_cat_under25,
      text = paste0("<b>", State, "</b><br>Burden: ", round(burden_under25, 1), "%<br>Category: ", burden_cat_under25, "<br>Annual Rent: $", format(round(median_rent_annual), big.mark = ","), "<br>Income (Under 25): $", format(round(income_under25), big.mark = ",")))) +
  geom_col(width = 0.75, alpha = 0.90) +
  geom_hline(yintercept = 30, linetype = "dashed", color = "#1a1a2e", linewidth = 0.7, alpha = 0.6) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "#c0392b", linewidth = 0.7, alpha = 0.6) +
  coord_flip() +
  scale_fill_manual(values = COLORS, name = "Burden Category") +
  scale_y_continuous(labels = label_percent(scale = 1)) +
  labs(x = NULL, y = "Rent Burden Ratio (%)") +
  theme_minimal(base_size = 11) +
  theme(axis.text.y = element_text(size = 8.5), legend.position = "top", panel.grid.minor = element_blank())

ggplotly(p5, tooltip = "text", height = 900) %>%
  layout(legend = list(orientation = "h", x = 0, y = 1.02),
         font = list(family = "sans-serif"), margin = list(l = 120))
```

```{=html}
<div class="conclusion-section">
  <h2>What This Means</h2>
  <p class="sub">Four conclusions grounded entirely in the data.</p>
  <div class="conclusion-grid">
    <div class="conclusion-card" style="border-color:#e74c3c;">
      <h4>College choice is a housing decision</h4>
      <p>California (48.3%), Hawaii (47.8%), and Florida (44.1%) are three of the most popular college destinations in the U.S. and also three of the least affordable states for young renters. Where you go to school determines how much of your income disappears into rent.</p>
    </div>
    <div class="conclusion-card" style="border-color:#e67e22;">
      <h4>The income gap is the real problem</h4>
      <p>Young renters are not paying dramatically higher rents than older adults. They are paying similar rents on dramatically lower incomes. The 2x burden gap is entirely an income gap, not a rent gap. Rents are not the villain. Low entry-level wages are.</p>
    </div>
    <div class="conclusion-card" style="border-color:#27ae60;">
      <h4>Affordable states are not accessible</h4>
      <p>Wyoming (23.3%) and North Dakota (24.0%) offer the lowest burden ratios in the country. But they also have some of the fewest universities, least entry-level opportunity, and lowest population density. Affordability and access to education almost never appear in the same state.</p>
    </div>
    <div class="conclusion-card" style="border-color:#3498db;">
      <h4>This gap will not resolve itself</h4>
      <p>The burden peaks during the exact years when young people are making foundational decisions about college, careers, and cities. Every under-25 renter making housing decisions today is navigating a system that was not designed with their income in mind.</p>
    </div>
  </div>
  <div class="final-statement">
    In 2023, <strong>34 out of 51 states</strong> cost-burdened young renters. <strong>Zero</strong> did the same to established adults. The data does not describe a housing crisis that affects everyone equally. It describes a generational fault line, where the same economy that works for adults aged 25 to 44 systematically fails adults under 25. That is not a coincidence. It is a structural condition.
  </div>
</div>

<div style="background:#f8f9fa;border-radius:16px;padding:24px;margin:30px 0;font-size:0.85em;color:#666;line-height:1.8;">
  <strong style="color:#1a1a2e;">Data Sources</strong><br>
  Income by Age of Householder: U.S. Census Bureau ACS 1-Year Estimates Table B19049 (2015-2023, excluding 2020)<br>
  Median Gross Rent: U.S. Census Bureau ACS 1-Year Estimates Table B25064 (2015-2023, excluding 2020)<br>
  Historical Household Income: U.S. Census Bureau CPS Historical Income Table H-8 (1984-2024)<br>
  Data accessed via tidycensus R package. Puerto Rico excluded. 2020 ACS 1-year estimates not released due to COVID-19 collection disruptions.<br>
  Analysis: Elma M., Jack D., Thusa. COMP/STAT 212, Macalester College, Spring 2026.
</div>
```
