---
author:
  - "Elma M."
  - "Jack D."
  - "Thusa"
date: today
format:
  html:
    page-layout: full
    toc: false
---

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

library(tidycensus)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(plotly)
library(leaflet)
library(tigris)
library(sf)
library(scales)
library(forcats)
library(htmltools)
library(ggrepel)
library(jsonlite)

readRenviron("~/.Renviron")
options(tigris_use_cache = TRUE)
```

```{r}
#| label: load-data
#| echo: false
#| message: false
#| warning: false
#| cache: true

years <- c(2015, 2016, 2017, 2018, 2019, 2021, 2022, 2023)

income_by_age_raw <- map_dfr(years, function(yr) {
  get_acs(geography="state",variables=c("under25"="B19049_002","age25_44"="B19049_003"),year=yr,survey="acs1") %>% mutate(year=yr)
})
rent_raw <- map_dfr(years, function(yr) {
  get_acs(geography="state",variables="B25064_001",year=yr,survey="acs1") %>% mutate(year=yr)
})

income_2023 <- income_by_age_raw %>%
  filter(year==2023) %>%
  select(State=NAME,variable,estimate) %>%
  pivot_wider(names_from=variable,values_from=estimate) %>%
  rename(income_under25=under25,income_25_44=age25_44)

rent_2023 <- rent_raw %>%
  filter(year==2023) %>%
  select(State=NAME,median_rent_monthly=estimate) %>%
  mutate(median_rent_annual=median_rent_monthly*12)

burden_2023 <- income_2023 %>%
  inner_join(rent_2023,by="State") %>%
  filter(State!="Puerto Rico") %>%
  mutate(
    burden_under25=(median_rent_annual/income_under25)*100,
    burden_cat_under25=case_when(burden_under25<30~"Affordable",burden_under25<50~"Burdened",TRUE~"Severely Burdened"),
    burden_25_44=(median_rent_annual/income_25_44)*100,
    burden_cat_25_44=case_when(burden_25_44<30~"Affordable",burden_25_44<50~"Burdened",TRUE~"Severely Burdened")
  ) %>%
  arrange(desc(burden_under25))

burden_all_years <- income_by_age_raw %>%
  filter(variable=="under25") %>%
  select(State=NAME,year,income_under25=estimate) %>%
  inner_join(rent_raw %>% select(State=NAME,year,median_rent_monthly=estimate) %>% mutate(median_rent_annual=median_rent_monthly*12),by=c("State","year")) %>%
  filter(State!="Puerto Rico") %>%
  mutate(burden_under25=(median_rent_annual/income_under25)*100) %>%
  arrange(State,year)
```

```{r}
#| label: build-jsons
#| echo: false
#| results: asis
#| message: false
#| warning: false

# Rent & Roster

# This chunk creates the JavaScript data objects used by all dropdown tools.
# jsonlite::toJSON is safer than manually pasting JSON strings.

rent_list <- setNames(
  as.list(round(burden_2023$median_rent_annual, 0)),
  burden_2023$State
)

vs_list <- burden_2023 %>%
  transmute(
    State,
    rent = round(median_rent_annual, 0),
    income = round(income_under25, 0),
    burden = round(burden_under25, 1),
    cat = burden_cat_under25
  ) %>%
  split(.$State) %>%
  purrr::map(~ .x %>% select(-State) %>% as.list())

universities <- data.frame(
  name=c("UCLA","UC Berkeley","Stanford University","USC","University of Miami","Florida State University","University of Florida","NYU","Columbia University","Cornell University","University of Texas Austin","Texas A&M","Rice University","University of Michigan","Michigan State University","University of Washington","University of Colorado Boulder","Arizona State University","University of Arizona","Georgia Tech","University of Georgia","University of Maryland","Georgetown University","University of Hawaii Manoa","Indiana University","Purdue University","University of Minnesota","University of Wisconsin Madison","Iowa State University","University of Iowa","University of Oregon","Oregon State University","Penn State University","University of Pennsylvania","University of North Carolina","NC State University","Louisiana State University","Tulane University","University of Alabama","Auburn University","University of Kentucky","University of Louisville","West Virginia University","University of Virginia","University of Nevada Las Vegas","University of New Mexico","University of Montana","University of Wyoming","University of Vermont","University of Rhode Island","University of Connecticut","University of South Carolina","Clemson University","University of Tennessee","Vanderbilt University","University of Arkansas","University of Oklahoma","Oklahoma State University","University of Nebraska Lincoln","University of North Dakota","North Dakota State University","Kansas State University","University of Kansas","University of Mississippi","Mississippi State University","University of Delaware","University of South Dakota","South Dakota State University","University of Maine","University of Idaho","University of Alaska Fairbanks","Macalester College","Harvard University","MIT","Boston University","Yale University","Princeton University","University of Chicago","Carnegie Mellon University","Ohio State University","Northwestern University","Emory University","University of Central Florida"),
  state=c("California","California","California","California","Florida","Florida","Florida","New York","New York","New York","Texas","Texas","Texas","Michigan","Michigan","Washington","Colorado","Arizona","Arizona","Georgia","Georgia","Maryland","District of Columbia","Hawaii","Indiana","Indiana","Minnesota","Wisconsin","Iowa","Iowa","Oregon","Oregon","Pennsylvania","Pennsylvania","North Carolina","North Carolina","Louisiana","Louisiana","Alabama","Alabama","Kentucky","Kentucky","West Virginia","Virginia","Nevada","New Mexico","Montana","Wyoming","Vermont","Rhode Island","Connecticut","South Carolina","South Carolina","Tennessee","Tennessee","Arkansas","Oklahoma","Oklahoma","Nebraska","North Dakota","North Dakota","Kansas","Kansas","Mississippi","Mississippi","Delaware","South Dakota","South Dakota","Maine","Idaho","Alaska","Minnesota","Massachusetts","Massachusetts","Massachusetts","Connecticut","New Jersey","Illinois","Pennsylvania","Ohio","Illinois","Georgia","Florida")
) %>% 
  left_join(
    burden_2023 %>% 
      select(State, burden_under25, burden_cat_under25, median_rent_annual, income_under25),
    by = c("state" = "State")
  )

uni_list <- universities %>%
  transmute(
    name,
    state,
    burden = round(burden_under25, 1),
    rent = round(median_rent_annual, 0),
    cat = burden_cat_under25
  ) %>%
  split(.$name) %>%
  purrr::map(~ .x %>% select(-name) %>% as.list())

tm_list <- burden_all_years %>%
  group_by(State) %>%
  arrange(year, .by_group = TRUE) %>%
  summarise(
    years = list(year),
    burdens = list(round(burden_under25, 1)),
    .groups = "drop"
  ) %>%
  split(.$State) %>%
  purrr::map(~ list(
    years = .x$years[[1]],
    burdens = .x$burdens[[1]]
  ))

cat(
  "<script>",
  "const CRD = ", jsonlite::toJSON(rent_list, auto_unbox = TRUE, na = "null"), ";",
  "const VSD = ", jsonlite::toJSON(vs_list, auto_unbox = TRUE, na = "null"), ";",
  "const UD = ", jsonlite::toJSON(uni_list, auto_unbox = TRUE, na = "null"), ";",
  "const TMD = ", jsonlite::toJSON(tm_list, auto_unbox = TRUE, na = "null"), ";",
  "</script>"
)
```

```{=html}
<style>
:root {
  --navy:    #0f1f3d;
  --navy2:   #1e3a5f;
  --blue:    #2563eb;
  --blue-lt: #dbeafe;
  --emerald: #059669;
  --em-lt:   #d1fae5;
  --amber:   #d97706;
  --am-lt:   #fef3c7;
  --slate:   #64748b;
  --light:   #f8fafc;
  --border:  #e2e8f0;
  --text:    #0f172a;
  --white:   #ffffff;
}
* { box-sizing: border-box; }

/* ── HERO ── */
.hero {
  background: linear-gradient(135deg, var(--navy) 0%, var(--navy2) 100%);
  color: white; padding: 72px 40px; text-align: center;
  margin: -20px -20px 48px -20px; border-radius: 0 0 16px 16px;
}
.hero h1 { font-size: 3em; font-weight: 800; margin: 0 0 10px 0; letter-spacing: -0.5px; }
.hero p  { font-size: 1.15em; opacity: 0.75; max-width: 560px; margin: 0 auto 36px auto; }
.stats-row { display: flex; justify-content: center; gap: 24px; flex-wrap: wrap; }
.stat-box {
  background: rgba(255,255,255,0.08); border: 1px solid rgba(255,255,255,0.12);
  border-radius: 12px; padding: 20px 28px; text-align: center; min-width: 140px;
}
.stat-number { font-size: 2.6em; font-weight: 800; color: #60a5fa; display: block; line-height: 1; }
.stat-label  { font-size: 0.78em; opacity: 0.65; margin-top: 6px; line-height: 1.4; }

/* ── SECTION HEADERS ── */
.section-title {
  font-size: 1.6em; font-weight: 700; color: var(--navy);
  margin: 56px 0 8px 0; border-left: 4px solid var(--blue); padding-left: 14px;
}
.section-subtitle { color: var(--slate); font-size: 1em; margin-bottom: 20px; padding-left: 18px; }

/* ── INTRO ── */
.intro-block {
  background: var(--light); border-radius: 16px; padding: 36px;
  margin: 24px 0; border: 1px solid var(--border);
  display: grid; grid-template-columns: 1fr 1fr; gap: 36px;
}
@media(max-width:768px){.intro-block{grid-template-columns:1fr;}}
.intro-block h3 { font-size: 1.05em; font-weight: 700; color: var(--navy); margin: 0 0 10px 0; }
.intro-block p  { color: #475569; line-height: 1.75; margin: 0 0 10px 0; font-size: 0.93em; }
.rq-list { list-style: none; padding: 0; margin: 0; }
.rq-list li {
  padding: 10px 14px; margin-bottom: 8px;
  background: var(--white); border-radius: 8px; border-left: 3px solid var(--blue);
  font-size: 0.88em; color: var(--text); line-height: 1.5;
}
.rq-num { font-weight: 700; color: var(--blue); margin-right: 6px; }
.team-row { display: flex; gap: 12px; margin-top: 14px; flex-wrap: wrap; }
.team-card {
  background: var(--white); border-radius: 10px; padding: 14px 18px;
  border-top: 2px solid var(--blue); flex: 1; min-width: 90px; text-align: center;
}
.team-card .name { font-weight: 700; color: var(--navy); font-size: 0.9em; }
.team-card .role { color: var(--slate); font-size: 0.75em; margin-top: 3px; }

/* ── PLOTS GRID ── */
.plots-grid { display: grid; grid-template-columns: 1fr 1fr; gap: 20px; margin: 24px 0; }
@media(max-width:768px){.plots-grid{grid-template-columns:1fr;}}
.plot-card {
  background: var(--white); border-radius: 12px; padding: 18px;
  box-shadow: 0 1px 6px rgba(0,0,0,0.06); border: 1px solid var(--border);
}
.plot-card h4 { font-size: 0.78em; font-weight: 600; color: var(--slate); margin: 0 0 10px 0; text-transform: uppercase; letter-spacing: 0.06em; }

/* ── TOOLS ── */
.tool-dark {
  background: var(--navy); border-radius: 16px; padding: 36px; color: white; margin: 16px 0;
}
.tool-slate {
  background: linear-gradient(135deg, #1e293b, #0f172a); border-radius: 16px; padding: 36px; color: white; margin: 16px 0;
}
.tool-title    { font-size: 1.25em; font-weight: 700; margin: 0 0 6px 0; }
.tool-subtitle { opacity: 0.6; margin-bottom: 24px; font-size: 0.88em; }
.tool-inputs   { display: flex; gap: 14px; flex-wrap: wrap; margin-bottom: 18px; }
.tool-ig       { flex: 1; min-width: 180px; }
.tool-ig label { display: block; font-size: 0.72em; font-weight: 600; margin-bottom: 6px; opacity: 0.65; text-transform: uppercase; letter-spacing: 0.06em; }
.tool-ig input, .tool-ig select {
  width: 100%; padding: 12px 14px; border: 1px solid rgba(255,255,255,0.15);
  border-radius: 8px; font-size: 14px; background: rgba(255,255,255,0.08); color: white; outline: none;
}
.tool-ig select option { background: #1e293b; color: white; }
.tool-ig input::placeholder { color: rgba(255,255,255,0.35); }
.tool-btn {
  background: var(--blue); color: white; border: none;
  padding: 12px 28px; border-radius: 8px; font-size: 14px; font-weight: 600;
  cursor: pointer; transition: 0.15s; white-space: nowrap;
}
.tool-btn:hover { background: #1d4ed8; transform: translateY(-1px); }
.result-box { margin-top: 20px; display: none; background: rgba(255,255,255,0.07); border-radius: 12px; padding: 20px; }

/* ── STATE VS STATE ── */
.vs-cards { display: grid; grid-template-columns: 1fr auto 1fr; gap: 14px; align-items: center; }
@media(max-width:580px){.vs-cards{grid-template-columns:1fr;}}
.vs-card { background: rgba(255,255,255,0.07); border: 1px solid rgba(255,255,255,0.1); border-radius: 12px; padding: 20px; text-align: center; }
.vs-card.winner { border-color: var(--emerald); background: rgba(5,150,105,0.1); }
.vs-state-name { font-size: 1em; font-weight: 700; margin-bottom: 10px; }
.vs-big-pct    { font-size: 2.4em; font-weight: 800; line-height: 1; margin-bottom: 4px; }
.vs-metric     { font-size: 0.8em; opacity: 0.65; line-height: 1.8; margin-top: 8px; }
.vs-vs         { font-size: 1.4em; font-weight: 700; opacity: 0.3; text-align: center; }
.vs-verdict    { margin-top: 16px; background: rgba(255,255,255,0.05); border-radius: 8px; padding: 14px 18px; font-size: 0.88em; line-height: 1.7; }

/* ── TIME MACHINE ── */
.tm-wrap { background: #0f172a; border-radius: 16px; padding: 36px; color: white; margin: 16px 0; }

/* ── HORIZONTAL SCROLL STORY ── */
.hstory-outer {
  position: relative;
  margin: 24px 0 48px 0;
}
.hstory-track {
  overflow-x: auto;
  scroll-snap-type: x mandatory;
  -webkit-overflow-scrolling: touch;
  display: flex;
  gap: 0;
  scrollbar-width: none;
  cursor: grab;
}
.hstory-track::-webkit-scrollbar { display: none; }
.hstory-track:active { cursor: grabbing; }

.hstory-panel {
  flex: 0 0 100%;
  scroll-snap-align: start;
  min-height: 340px;
  display: flex;
  align-items: center;
  justify-content: center;
  padding: 48px 32px;
  border-radius: 16px;
  position: relative;
  transition: opacity 0.3s;
}
.hsp-1 { background: linear-gradient(135deg, #0f1f3d, #1e3a5f); color: white; }
.hsp-2 { background: linear-gradient(135deg, #064e3b, #065f46); color: white; }
.hsp-3 { background: linear-gradient(135deg, #1e3a5f, #1e40af); color: white; }
.hsp-4 { background: linear-gradient(135deg, #1a1a2e, #16213e); color: white; }

.hstory-inner { max-width: 600px; width: 100%; text-align: center; }

.hs-giant {
  font-size: clamp(6em, 18vw, 11em);
  font-weight: 800;
  line-height: 0.9;
  letter-spacing: -3px;
  display: block;
  margin-bottom: 20px;
}
.hs-giant.c-blue    { color: #60a5fa; }
.hs-giant.c-emerald { color: #34d399; }
.hs-giant.c-indigo  { color: #818cf8; }

.hs-head { font-size: 1.2em; font-weight: 700; margin-bottom: 12px; opacity: 0.95; line-height: 1.3; }
.hs-body { font-size: 0.9em; opacity: 0.7; line-height: 1.75; max-width: 480px; margin: 0 auto; }
.hs-accent-b { color: #93c5fd; font-weight: 600; }
.hs-accent-g { color: #6ee7b7; font-weight: 600; }

/* bars in panel 4 */
.hs-bars { display: flex; gap: 16px; justify-content: center; align-items: flex-end; height: 120px; margin: 24px auto 16px; }
.hs-bar-col { display: flex; flex-direction: column; align-items: center; gap: 6px; }
.hs-bar {
  width: 48px; border-radius: 4px 4px 0 0;
  transition: height 0.9s cubic-bezier(0.34,1.56,0.64,1);
}
.hs-bar-pct { font-size: 0.82em; font-weight: 700; }
.hs-bar-lbl { font-size: 0.7em; opacity: 0.6; text-align: center; line-height: 1.2; }

/* nav dots */
.hstory-dots {
  display: flex; justify-content: center; gap: 8px; margin-top: 16px;
}
.hstory-dot {
  width: 8px; height: 8px; border-radius: 50%;
  background: var(--border); cursor: pointer; transition: all 0.2s;
  border: none; padding: 0;
}
.hstory-dot.active { background: var(--blue); transform: scale(1.3); }

/* nav arrows */
.hstory-nav {
  display: flex; justify-content: space-between; align-items: center;
  margin-top: 14px; padding: 0 4px;
}
.hstory-arrow {
  background: none; border: 1px solid var(--border); border-radius: 8px;
  padding: 8px 16px; font-size: 0.85em; color: var(--slate);
  cursor: pointer; transition: 0.15s; font-weight: 600;
}
.hstory-arrow:hover { background: var(--light); color: var(--navy); }
.hstory-arrow:disabled { opacity: 0.3; cursor: not-allowed; }
.hstory-counter { font-size: 0.82em; color: var(--slate); }

/* ── CONCLUSIONS ── */
.conclusion-wrap {
  background: var(--navy); color: white;
  border-radius: 16px; padding: 48px 40px; margin: 40px 0;
}
.conclusion-wrap h2 { font-size: 1.8em; font-weight: 800; margin: 0 0 6px 0; }
.conclusion-wrap .sub { opacity: 0.5; margin-bottom: 28px; font-size: 0.9em; }
.conc-grid { display: grid; grid-template-columns: repeat(auto-fit,minmax(220px,1fr)); gap: 16px; margin-bottom: 28px; }
.conc-card { background: rgba(255,255,255,0.06); border-radius: 12px; padding: 20px; border-top: 2px solid; }
.conc-card h4 { margin: 0 0 8px 0; color: white; font-size: 0.88em; font-weight: 700; }
.conc-card p  { margin: 0; color: rgba(255,255,255,0.6); font-size: 0.82em; line-height: 1.65; }
.final-stmt {
  background: rgba(37,99,235,0.15); border-radius: 12px; padding: 22px 26px;
  border-left: 3px solid var(--blue); font-size: 0.95em; line-height: 1.8;
  color: rgba(255,255,255,0.85);
}

/* ─────────────────────────────────────────────
   FINAL VISUAL UPDATE ONLY
   Soft background + screenshot-style top header.
───────────────────────────────────────────── */

html {
  scroll-behavior: smooth;
}

body {
  background:
    radial-gradient(circle at 8% 8%, rgba(96,165,250,0.13), transparent 28%),
    radial-gradient(circle at 92% 12%, rgba(148,163,184,0.10), transparent 30%),
    radial-gradient(circle at 88% 82%, rgba(251,191,36,0.08), transparent 32%),
    linear-gradient(135deg, #f5f9ff 0%, #f8fafc 25%, #fffaf5 52%, #fff7ed 76%, #fefce8 100%);
  background-attachment: fixed;
  color: var(--text);
  position: relative;
  overflow-x: hidden;
}

.hero {
  display: none !important;
}

.top-hero {
  margin: -20px -20px 42px -20px;
  padding: 22px 42px 28px 42px;
  min-height: 135px;
  color: white;
  position: relative;
  overflow: hidden;
  background:
    radial-gradient(circle at 10% 20%, rgba(96,165,250,0.16), transparent 28%),
    radial-gradient(circle at 85% 18%, rgba(148,163,184,0.14), transparent 30%),
    linear-gradient(105deg, #061b3a 0%, #0f274f 38%, #2d3748 70%, #475569 100%);
  border-radius: 0 0 20px 20px;
  box-shadow: 0 12px 38px rgba(15,23,42,0.16), 0 4px 12px rgba(15,23,42,0.08);
}

.top-hero::before {
  content: "";
  position: absolute;
  inset: 0;
  background:
    radial-gradient(circle at 8% 35%, rgba(255,255,255,0.12) 0 2px, transparent 3px),
    radial-gradient(circle at 88% 40%, rgba(255,255,255,0.08) 0 2px, transparent 3px);
  background-size: 180px 180px;
  opacity: 0.32;
  pointer-events: none;
}

.top-hero::after {
  content: "";
  position: absolute;
  left: 18%;
  right: -8%;
  bottom: 10px;
  height: 80px;
  background: linear-gradient(90deg, transparent, rgba(96,165,250,0.16), rgba(148,163,184,0.10), transparent);
  filter: blur(18px);
  opacity: 0.75;
  pointer-events: none;
}

.top-nav-wrap {
  position: relative;
  z-index: 2;
  display: flex;
  justify-content: space-between;
  align-items: flex-start;
  gap: 32px;
}

.brand-block {
  display: flex;
  flex-direction: column;
}

.brand-title {
  display: flex;
  align-items: center;
  gap: 14px;
  font-size: 2.45em;
  font-weight: 900;
  line-height: 1;
  letter-spacing: -0.02em;
  text-shadow: 0 2px 10px rgba(0,0,0,0.22);
}

.brand-icon {
  font-size: 0.92em;
}

.brand-title .amp {
  color: #94a3b8;
}

.brand-subtitle {
  margin-top: 12px;
  font-size: 1.04em;
  color: rgba(255,255,255,0.82);
  letter-spacing: 0.01em;
}

.nav-links {
  display: flex;
  align-items: center;
  gap: 34px;
  padding-top: 18px;
  flex-wrap: wrap;
  justify-content: flex-end;
}

.nav-links a {
  color: rgba(255,255,255,0.92);
  text-decoration: none;
  text-transform: uppercase;
  font-size: 0.82em;
  font-weight: 800;
  letter-spacing: 0.04em;
  transition: all 0.18s ease;
}

.nav-links a:hover {
  color: #cbd5e1;
  transform: translateY(-1px);
}

.intro-block,
.plot-card,
.team-card {
  background: rgba(255,255,255,0.86) !important;
  backdrop-filter: blur(16px);
  -webkit-backdrop-filter: blur(16px);
  border: 1px solid rgba(255,255,255,0.75) !important;
  box-shadow: 0 18px 45px rgba(15,23,42,0.08), 0 4px 12px rgba(15,23,42,0.05) !important;
}

.tool-dark,
.tool-slate,
.tm-wrap,
.conclusion-wrap,
.hstory-panel,
.conc-card {
  box-shadow: 0 18px 45px rgba(15,23,42,0.09), 0 4px 12px rgba(15,23,42,0.05) !important;
}

.section-title {
  background: linear-gradient(90deg, #0f3e78, #64748b, #0f172a);
  -webkit-background-clip: text;
  -webkit-text-fill-color: transparent;
  border-left: 4px solid #64748b !important;
}

.section-title::after {
  content: "";
  display: block;
  width: 145px;
  height: 2px;
  margin-top: 10px;
  border-radius: 999px;
  background: linear-gradient(90deg, #60a5fa, #94a3b8, transparent);
}

.rq-list li,
.team-card {
  border-left-color: #64748b !important;
}

.team-card {
  border-top-color: #64748b !important;
}

.rq-num {
  color: #64748b !important;
}

.tool-dark {
  background:
    radial-gradient(circle at top left, rgba(96,165,250,0.16), transparent 34%),
    radial-gradient(circle at bottom right, rgba(148,163,184,0.10), transparent 38%),
    linear-gradient(135deg, #0f172a, #172554 54%, #334155) !important;
}

.tool-slate {
  background:
    radial-gradient(circle at top right, rgba(148,163,184,0.10), transparent 36%),
    linear-gradient(135deg, #1e293b, #172554 50%, #334155 100%) !important;
}

.tm-wrap {
  background:
    radial-gradient(circle at top left, rgba(96,165,250,0.16), transparent 36%),
    radial-gradient(circle at bottom right, rgba(148,163,184,0.10), transparent 36%),
    linear-gradient(135deg, #0f172a, #1e3a8a 52%, #334155) !important;
}

.hsp-1 { background: linear-gradient(135deg, #082f66, #1d4ed8, #475569) !important; }
.hsp-2 { background: linear-gradient(135deg, #0f172a, #0f766e, #475569) !important; }
.hsp-3 { background: linear-gradient(135deg, #1e1b4b, #2563eb, #475569) !important; }
.hsp-4 { background: linear-gradient(135deg, #111827, #0f172a, #334155) !important; }

.conclusion-wrap {
  background:
    radial-gradient(circle at top right, rgba(148,163,184,0.12), transparent 35%),
    radial-gradient(circle at bottom left, rgba(96,165,250,0.16), transparent 35%),
    linear-gradient(135deg, #0f172a, #172554 56%, #334155) !important;
}

.tool-btn {
  background: linear-gradient(135deg, #2563eb, #64748b) !important;
  box-shadow: 0 6px 18px rgba(217,130,43,0.18);
}

.tool-btn:hover {
  background: linear-gradient(135deg, #1d4ed8, #475569) !important;
  transform: translateY(-1px);
}

.hstory-dot.active {
  background: #64748b !important;
}

.final-stmt {
  background: linear-gradient(135deg, rgba(37,99,235,0.16), rgba(217,130,43,0.14)) !important;
  border-left-color: #64748b !important;
}

@media(max-width: 980px) {
  .top-nav-wrap {
    flex-direction: column;
  }

  .nav-links {
    justify-content: flex-start;
    gap: 18px;
    padding-top: 10px;
  }

  .brand-title {
    font-size: 2em;
  }
}

</style>


<div class="top-hero">
  <div class="top-nav-wrap">
    <div class="brand-block">
      <div class="brand-title">
        <span class="brand-icon">🏠</span>
        <span>RENT <span class="amp">&amp;</span> ROSTER</span>
      </div>
      <div class="brand-subtitle">
        Can college-age renters actually afford to live in the U.S.?
      </div>
    </div>

    <div class="nav-links">
      <a href="#should-i-go-there">Should I Go There?</a>
      <a href="#state-vs-state">State vs State</a>
      <a href="#rent-burden-time-machine">Time Machine</a>
      <a href="#the-story-in-numbers">Story</a>
      <a href="#conclusion">Conclusion</a>
      <a href="#about-this-project">About Us</a>
    </div>
  </div>
</div>

<div class="hero">
  <h1>Can You Afford to Rent?</h1>
  <p>A data investigation into student housing affordability across all 50 U.S. states</p>
  <div class="stats-row">
    <div class="stat-box"><span class="stat-number" id="c1">0</span><div class="stat-label">states burden<br>young renters</div></div>
    <div class="stat-box"><span class="stat-number" id="c2">0%</span><div class="stat-label">average burden<br>under-25</div></div>
    <div class="stat-box"><span class="stat-number" id="c3">0</span><div class="stat-label">states burden<br>ages 25-44</div></div>
    <div class="stat-box"><span class="stat-number" id="c4">0x</span><div class="stat-label">higher burden<br>young vs older</div></div>
  </div>
</div>

<script>
function animCount(id,target,suffix,dur){const el=document.getElementById(id);let v=0;const step=target/(dur/16);const t=setInterval(()=>{v+=step;if(v>=target){el.textContent=target+suffix;clearInterval(t);}else{el.textContent=Math.floor(v)+suffix;}},16);}
window.addEventListener("load",()=>{setTimeout(()=>{animCount("c1",34,"",1400);animCount("c2",34,"%",1400);animCount("c3",0,"",400);animCount("c4",2,"x",900);},300);});
function getColor(r){if(r<30)return"#059669";if(r<50)return"#d97706";return"#dc2626";}
function drawGauge(ratio,cid){
  const color=getColor(ratio);
  const angle=Math.min((ratio/60)*180,180);
  const rad=(angle-180)*Math.PI/180;
  const x=100+80*Math.cos(rad);const y=100+80*Math.sin(rad);
  const el=document.getElementById(cid);if(!el)return;
  el.innerHTML=`<svg width="200" height="110" viewBox="0 0 200 110">
    <path d="M 20 100 A 80 80 0 0 1 180 100" fill="none" stroke="#e2e8f0" stroke-width="14" stroke-linecap="round"/>
    <path d="M 20 100 A 80 80 0 0 1 180 100" fill="none" stroke="${color}" stroke-width="14" stroke-linecap="round" stroke-dasharray="${angle*80*Math.PI/180} 1000"/>
    <line x1="100" y1="100" x2="${x}" y2="${y}" stroke="white" stroke-width="2.5" stroke-linecap="round"/>
    <circle cx="100" cy="100" r="4" fill="white"/>
    <text x="100" y="72" text-anchor="middle" font-size="20" font-weight="700" fill="${color}">${ratio}%</text>
    <text x="20" y="112" font-size="8" fill="rgba(255,255,255,0.4)">0%</text>
    <text x="88" y="22" font-size="8" fill="rgba(255,255,255,0.4)">30%</text>
    <text x="170" y="112" font-size="8" fill="rgba(255,255,255,0.4)">60%</text>
  </svg>`;
}
</script>
```

<div class="section-title" id="about-this-project">About This Project</div>

```{=html}
<div class="intro-block">
  <div>
    <h3>What We Set Out to Answer</h3>
    <p>All three of us are students navigating housing costs right now. We had a simple question: is what we are living through measurable, and is it systematically worse for students than for everyone else?</p>
    <p>We pulled data from the U.S. Census Bureau American Community Survey covering rent and income by age group across all 51 states.</p>
    <div class="team-row">
      <div class="team-card"><div class="name">Elma M.</div><div class="role">EDA Lead</div></div>
      <div class="team-card"><div class="name">Jack D.</div><div class="role">Income Analysis</div></div>
      <div class="team-card"><div class="name">Thusa</div><div class="role">Trend Analysis</div></div>
    </div>
  </div>
  <div>
    <h3>Research Questions</h3>
    <ul class="rq-list">
      <li><span class="rq-num">01</span>Which states are most and least affordable for college-age renters aged 18 to 24 compared to adults aged 25 to 44?</li>
      <li><span class="rq-num">02</span>What is the rent burden ratio for under-25 householders by state, and how many states fall into burdened or severely burdened categories?</li>
      <li><span class="rq-num">03</span>How has the affordability gap changed over time, and which states show the biggest generational disparities?</li>
    </ul>
    <p style="margin-top:12px;font-size:0.8em;color:#94a3b8;">ACS 1-Year Estimates B19049 + B25064, 2015-2023 (excl. 2020). Census H-8. Via tidycensus.</p>
  </div>
</div>
```

<div class="section-title">The Map</div>
<div class="section-subtitle">States colored by rent burden for under-25 renters. Click any pin to see details.</div>

```{r}
#| label: university-map
#| echo: false
#| message: false
#| warning: false

uni_map_df <- data.frame(
  name=c("UCLA","UC Berkeley","Stanford University","USC","University of Miami","Florida State University","University of Florida","NYU","Columbia University","Cornell University","University of Texas Austin","Texas A&M","Rice University","University of Michigan","Michigan State University","University of Washington","University of Colorado Boulder","Arizona State University","University of Arizona","Georgia Tech","University of Georgia","University of Maryland","Georgetown University","University of Hawaii Manoa","Indiana University","Purdue University","University of Minnesota","University of Wisconsin Madison","Iowa State University","University of Iowa","University of Oregon","Oregon State University","Penn State University","University of Pennsylvania","University of North Carolina","NC State University","Louisiana State University","Tulane University","University of Alabama","Auburn University","University of Kentucky","University of Louisville","West Virginia University","University of Virginia","University of Nevada Las Vegas","University of New Mexico","University of Montana","University of Wyoming","University of Vermont","University of Rhode Island","University of Connecticut","University of South Carolina","Clemson University","University of Tennessee","Vanderbilt University","University of Arkansas","University of Oklahoma","Oklahoma State University","University of Nebraska Lincoln","University of North Dakota","North Dakota State University","Kansas State University","University of Kansas","University of Mississippi","Mississippi State University","University of Delaware","University of South Dakota","South Dakota State University","University of Maine","University of Idaho","University of Alaska Fairbanks","Macalester College","Harvard University","MIT","Boston University","Yale University","Princeton University","University of Chicago","Carnegie Mellon University","Ohio State University","Northwestern University","Emory University","University of Central Florida"),
  state=c("California","California","California","California","Florida","Florida","Florida","New York","New York","New York","Texas","Texas","Texas","Michigan","Michigan","Washington","Colorado","Arizona","Arizona","Georgia","Georgia","Maryland","District of Columbia","Hawaii","Indiana","Indiana","Minnesota","Wisconsin","Iowa","Iowa","Oregon","Oregon","Pennsylvania","Pennsylvania","North Carolina","North Carolina","Louisiana","Louisiana","Alabama","Alabama","Kentucky","Kentucky","West Virginia","Virginia","Nevada","New Mexico","Montana","Wyoming","Vermont","Rhode Island","Connecticut","South Carolina","South Carolina","Tennessee","Tennessee","Arkansas","Oklahoma","Oklahoma","Nebraska","North Dakota","North Dakota","Kansas","Kansas","Mississippi","Mississippi","Delaware","South Dakota","South Dakota","Maine","Idaho","Alaska","Minnesota","Massachusetts","Massachusetts","Massachusetts","Connecticut","New Jersey","Illinois","Pennsylvania","Ohio","Illinois","Georgia","Florida"),
  lat=c(34.0689,37.8724,37.4275,34.0224,25.7142,30.4420,29.6465,40.7295,40.8075,42.4534,30.2849,30.6187,29.7174,42.2780,42.7009,47.6553,40.0076,33.4255,32.2319,33.7756,33.9480,38.9869,38.9076,21.2969,39.1682,40.4259,44.9740,43.0753,42.0140,41.6611,44.0460,44.5646,40.7982,39.9526,35.9049,35.7847,30.4133,29.9384,33.2148,32.6099,38.0473,38.2527,39.6350,38.0336,36.1140,35.0844,46.8625,42.8666,44.4759,41.4801,41.8084,33.9979,34.6834,35.9546,36.1447,36.0671,35.2076,36.1156,40.8202,47.9219,46.8974,39.1836,38.9543,34.3648,33.4554,39.6784,43.0760,44.3168,44.9015,46.7196,64.8581,44.9375,42.3770,42.3601,42.3505,41.3163,40.3430,41.7886,40.4444,40.0076,42.0565,33.7925,28.6024),
  lng=c(-118.4452,-122.2595,-122.1697,-118.2851,-80.2790,-84.2980,-82.3520,-73.9965,-73.9626,-76.4735,-97.7341,-96.3365,-95.4019,-83.7382,-84.4821,-122.3035,-105.2659,-111.9400,-110.9501,-84.3963,-83.3776,-76.9426,-77.0735,-157.8167,-86.5230,-86.9081,-93.2350,-89.4012,-93.6465,-91.5550,-123.0694,-123.2780,-77.8600,-75.1932,-79.0469,-78.6785,-91.1800,-90.1183,-87.5450,-85.4808,-84.5047,-85.7585,-79.9559,-78.5080,-115.1398,-106.6504,-114.0120,-108.9658,-73.1937,-71.5274,-72.2495,-81.0219,-82.8374,-83.9274,-86.8025,-94.1792,-97.4395,-96.5925,-96.7005,-101.9971,-96.7833,-96.5717,-95.2483,-89.5377,-88.7873,-75.7497,-96.9040,-96.8022,-68.9675,-116.9190,-147.8469,-93.1710,-71.1167,-71.0942,-71.1054,-72.9223,-74.6514,-87.5987,-79.9532,-83.0300,-87.6753,-84.3267,-81.2001)
) %>%
  left_join(burden_2023 %>% select(State,burden_under25,burden_cat_under25,median_rent_annual,income_under25),by=c("state"="State")) %>%
  mutate(
    bg=case_when(burden_under25<30~"#d1fae5",burden_under25<50~"#fef3c7",TRUE~"#fee2e2"),
    tc=case_when(burden_under25<30~"#065f46",burden_under25<50~"#92400e",TRUE~"#991b1b"),
    popup_text=paste0("<div style='font-family:sans-serif;min-width:210px;padding:4px;'><div style='font-size:1em;font-weight:700;color:#0f172a;margin-bottom:3px;'>",name,"</div><div style='font-size:0.78em;color:#64748b;margin-bottom:8px;'>",state,"</div><div style='background:",bg,";padding:10px;border-radius:8px;margin-bottom:8px;text-align:center;'><div style='font-size:1.8em;font-weight:800;color:",tc,";'>",round(burden_under25,1),"%</div><div style='font-size:0.72em;color:",tc,";'>rent burden for under-25</div></div><div style='font-size:0.8em;line-height:1.8;'><b>Annual Rent:</b> $",format(round(median_rent_annual),big.mark=","),"<br><b>Under-25 Income:</b> $",format(round(income_under25),big.mark=","),"</div></div>"),
    mc=case_when(burden_under25<30~"green",burden_under25<50~"orange",TRUE~"red")
  )

states_sf2 <- tigris::states(cb=TRUE,resolution="20m",year=2022) %>%
  filter(!STUSPS %in% c("PR","GU","VI","MP","AS")) %>%
  sf::st_transform(crs=4326) %>%
  left_join(burden_2023,by=c("NAME"="State"))

pal2 <- colorNumeric(palette=c("#059669","#d97706","#dc2626"),domain=c(10,55))
ig <- makeAwesomeIcon(icon="graduation-cap",library="fa",markerColor="green",iconColor="white")
io <- makeAwesomeIcon(icon="graduation-cap",library="fa",markerColor="orange",iconColor="white")
ir <- makeAwesomeIcon(icon="graduation-cap",library="fa",markerColor="red",iconColor="white")

m <- leaflet(states_sf2) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor=~pal2(burden_under25),fillOpacity=0.6,color="white",weight=1,smoothFactor=0.5,
    label=~paste0(NAME,": ",round(burden_under25,1),"% burden") %>% lapply(htmltools::HTML),
    labelOptions=labelOptions(style=list("font-weight"="600",padding="3px 8px"),textsize="12px")) %>%
  addLegend(pal=pal2,values=~burden_under25,title="Rent Burden %<br><small>Under-25 Householders</small>",position="bottomleft",labFormat=labelFormat(suffix="%"))

ug<-uni_map_df%>%filter(mc=="green"); uo<-uni_map_df%>%filter(mc=="orange"); ur<-uni_map_df%>%filter(mc=="red")
if(nrow(ug)>0) m<-m%>%addAwesomeMarkers(data=ug,lng=~lng,lat=~lat,icon=ig,popup=~popup_text,label=~name,group="Affordable")
if(nrow(uo)>0) m<-m%>%addAwesomeMarkers(data=uo,lng=~lng,lat=~lat,icon=io,popup=~popup_text,label=~name,group="Burdened")
if(nrow(ur)>0) m<-m%>%addAwesomeMarkers(data=ur,lng=~lng,lat=~lat,icon=ir,popup=~popup_text,label=~name,group="Severely Burdened")
m%>%addLayersControl(overlayGroups=c("Affordable","Burdened","Severely Burdened"),options=layersControlOptions(collapsed=FALSE))%>%setView(lng=-96,lat=38,zoom=4)
```

<div class="section-title">Exploratory Data Analysis</div>
<div class="section-subtitle">Four views into the 2023 rent burden data.</div>

```{r}
#| label: eda-plots
#| echo: false
#| message: false
#| warning: false

COLORS_EDA <- c("Affordable (<30%)"="#059669","Burdened (30-50%)"="#d97706","Severely Burdened (>50%)"="#dc2626")
theme_rb <- function(){
  theme_minimal(base_size=12)+
  theme(plot.title=element_text(face="bold",size=12,color="#0f1f3d"),
        plot.subtitle=element_text(size=9.5,color="#64748b"),
        panel.grid.minor=element_blank(),
        panel.grid.major=element_line(color="#f1f5f9"),
        legend.position="top",
        plot.background=element_rect(fill="white",color=NA),
        panel.background=element_rect(fill="white",color=NA),
        plot.margin=margin(12,14,10,12))
}

burden_eda <- burden_2023 %>%
  mutate(burden_cat_under25=case_when(burden_under25<30~"Affordable (<30%)",burden_under25<50~"Burdened (30-50%)",TRUE~"Severely Burdened (>50%)"))

p1 <- ggplot(burden_eda,aes(x=burden_under25,fill=burden_cat_under25))+
  geom_histogram(bins=18,color="white",linewidth=0.3,alpha=0.9)+
  geom_vline(xintercept=30,linetype="dashed",color="#0f1f3d",linewidth=0.7)+
  annotate("text",x=31,y=7.5,label="30%",hjust=0,size=2.8,color="#0f1f3d",fontface="italic")+
  scale_fill_manual(values=COLORS_EDA,name=NULL)+
  scale_x_continuous(labels=label_percent(scale=1))+
  labs(title="Burden Distribution",subtitle="Under-25 householders by state (2023)",x="Rent Burden Ratio",y="States")+theme_rb()

p2 <- burden_eda%>%slice_head(n=10)%>%
  ggplot(aes(x=fct_reorder(State,burden_under25),y=burden_under25,fill=burden_cat_under25))+
  geom_col(width=0.7,alpha=0.9)+
  geom_text(aes(label=paste0(round(burden_under25,1),"%")),hjust=-0.1,size=2.6,fontface="bold",color="#0f1f3d")+
  coord_flip(clip="off")+scale_fill_manual(values=COLORS_EDA,name=NULL)+
  scale_y_continuous(limits=c(0,56),labels=label_percent(scale=1))+
  labs(title="Least Affordable States",subtitle="Highest burden for under-25 (2023)",x=NULL,y="Burden %")+theme_rb()+theme(legend.position="none")

p3 <- burden_eda%>%slice_tail(n=10)%>%
  ggplot(aes(x=fct_reorder(State,burden_under25),y=burden_under25,fill=burden_cat_under25))+
  geom_col(width=0.7,alpha=0.9)+
  geom_text(aes(label=paste0(round(burden_under25,1),"%")),hjust=-0.1,size=2.6,fontface="bold",color="#0f1f3d")+
  coord_flip(clip="off")+scale_fill_manual(values=COLORS_EDA,name=NULL)+
  scale_y_continuous(limits=c(0,33),labels=label_percent(scale=1))+
  labs(title="Most Affordable States",subtitle="Lowest burden for under-25 (2023)",x=NULL,y="Burden %")+theme_rb()+theme(legend.position="none")

p6 <- ggplot(burden_eda,aes(x=income_under25,y=median_rent_annual,color=burden_cat_under25,label=State))+
  geom_abline(slope=0.30,intercept=0,linetype="dashed",color="#059669",linewidth=0.7)+
  geom_abline(slope=0.50,intercept=0,linetype="dashed",color="#dc2626",linewidth=0.7)+
  geom_point(size=2.5,alpha=0.85)+
  geom_text_repel(data=burden_eda%>%filter(burden_under25>40|burden_under25<26),size=2.4,color="#334155",max.overlaps=14,segment.color="#cbd5e1")+
  scale_color_manual(values=COLORS_EDA,name=NULL)+
  scale_x_continuous(labels=label_dollar())+scale_y_continuous(labels=label_dollar())+
  labs(title="Income vs. Rent",subtitle="Each dot = one state. Above dashed lines = cost-burdened.",x="Median Income (Under-25)",y="Median Annual Rent")+theme_rb()
```

```{=html}
<div class="plots-grid">
  <div class="plot-card"><h4>Burden Distribution</h4>
```
```{r}
#| echo: false
#| fig-height: 3.8
print(p1)
```
```{=html}
  </div><div class="plot-card"><h4>Income vs. Rent</h4>
```
```{r}
#| echo: false
#| fig-height: 3.8
print(p6)
```
```{=html}
  </div><div class="plot-card"><h4>Least Affordable</h4>
```
```{r}
#| echo: false
#| fig-height: 3.8
print(p2)
```
```{=html}
  </div><div class="plot-card"><h4>Most Affordable</h4>
```
```{r}
#| echo: false
#| fig-height: 3.8
print(p3)
```
```{=html}
  </div>
</div>
```

<div class="section-title">The Generational Gap</div>
<div class="section-subtitle">Every established adult is affordable. Two thirds of young renters are not.</div>

```{r}
#| label: gen-gap
#| echo: false
#| message: false
#| warning: false

burden_long <- burden_2023 %>%
  select(State,burden_under25,burden_25_44) %>%
  pivot_longer(c(burden_under25,burden_25_44),names_to="age_group",values_to="burden_ratio") %>%
  mutate(age_group=recode(age_group,"burden_under25"="Under 25 (college-age)","burden_25_44"="Ages 25-44 (established adults)"))

p4 <- ggplot(burden_long,aes(x=burden_ratio,fill=age_group,text=paste0(age_group,"<br>Burden: ",round(burden_ratio,1),"%")))+
  geom_histogram(bins=20,color="white",linewidth=0.3,alpha=0.82,position="identity")+
  geom_vline(xintercept=30,linetype="dashed",color="#0f1f3d",linewidth=0.8)+
  geom_vline(xintercept=50,linetype="dashed",color="#dc2626",linewidth=0.8)+
  annotate("rect",xmin=30,xmax=50,ymin=0,ymax=Inf,alpha=0.04,fill="#d97706")+
  annotate("rect",xmin=50,xmax=Inf,ymin=0,ymax=Inf,alpha=0.06,fill="#dc2626")+
  annotate("text",x=31,y=15,label="Burdened zone",hjust=0,size=3,color="#d97706",fontface="italic")+
  scale_fill_manual(values=c("Under 25 (college-age)"="#2563eb","Ages 25-44 (established adults)"="#059669"),name="Age Group")+
  scale_x_continuous(labels=label_percent(scale=1))+
  labs(x="Rent Burden Ratio",y="Number of States",caption="ACS 1-Year Estimates B19049 + B25064, 2023")+
  theme_minimal(base_size=12)+theme(legend.position="top",panel.grid.minor=element_blank(),panel.grid.major=element_line(color="#f1f5f9"))

ggplotly(p4,tooltip="text")%>%layout(legend=list(orientation="h",x=0.05,y=1.12),font=list(family="sans-serif"))
```

<div class="section-title" id="the-story-in-numbers">The Story in Numbers</div>
<div class="section-subtitle">Swipe or use the arrows to move through the data one fact at a time.</div>

```{=html}
<div class="hstory-outer">
  <div class="hstory-track" id="htrack">

    <!-- Panel 1 -->
    <div class="hstory-panel hsp-1">
      <div class="hstory-inner">
        <span class="hs-giant c-blue" id="hs-34">34</span>
        <div class="hs-head">states cost-burden young renters</div>
        <div class="hs-body">In <span class="hs-accent-b">34 out of 51 states</span>, a typical under-25 householder spends more than 30 cents of every earned dollar on rent alone. That is two thirds of the country.</div>
      </div>
    </div>

    <!-- Panel 2 -->
    <div class="hstory-panel hsp-2">
      <div class="hstory-inner">
        <span class="hs-giant c-emerald">0</span>
        <div class="hs-head">states cost-burden adults aged 25 to 44</div>
        <div class="hs-body"><span class="hs-accent-g">Not a single one.</span> The same rents that drain young budgets are entirely manageable once income catches up. The problem is not rent. It is income.</div>
      </div>
    </div>

    <!-- Panel 3 -->
    <div class="hstory-panel hsp-3">
      <div class="hstory-inner">
        <span class="hs-giant c-indigo">2×</span>
        <div class="hs-head">higher burden for young renters than established adults</div>
        <div class="hs-body">Average burden for under-25: <span class="hs-accent-b">33.7%</span>. Average for ages 25 to 44: <span class="hs-accent-g">17.8%</span>. Same apartments. Same cities. Very different realities.</div>
      </div>
    </div>

    <!-- Panel 4 -->
    <div class="hstory-panel hsp-4">
      <div class="hstory-inner">
        <div class="hs-head">The gap is widest in the most popular college states</div>
        <div class="hs-bars" id="hs-bars">
          <div class="hs-bar-col">
            <div class="hs-bar-pct" style="color:#f87171">48.3%</div>
            <div class="hs-bar" style="background:#ef4444;height:0px;" data-h="110"></div>
            <div class="hs-bar-lbl">Cali&shy;fornia</div>
          </div>
          <div class="hs-bar-col">
            <div class="hs-bar-pct" style="color:#f87171">47.8%</div>
            <div class="hs-bar" style="background:#ef4444;height:0px;" data-h="108"></div>
            <div class="hs-bar-lbl">Hawaii</div>
          </div>
          <div class="hs-bar-col">
            <div class="hs-bar-pct" style="color:#94a3b8">44.1%</div>
            <div class="hs-bar" style="background:#64748b;height:0px;" data-h="100"></div>
            <div class="hs-bar-lbl">Florida</div>
          </div>
          <div class="hs-bar-col">
            <div class="hs-bar-pct" style="color:#60a5fa">30.1%</div>
            <div class="hs-bar" style="background:#3b82f6;height:0px;" data-h="68"></div>
            <div class="hs-bar-lbl">Minne&shy;sota</div>
          </div>
          <div class="hs-bar-col">
            <div class="hs-bar-pct" style="color:#34d399">23.3%</div>
            <div class="hs-bar" style="background:#10b981;height:0px;" data-h="53"></div>
            <div class="hs-bar-lbl">Wyoming</div>
          </div>
        </div>
        <div class="hs-body">Choosing where to study is inseparable from choosing how much of your income disappears into rent.</div>
      </div>
    </div>

  </div>

  <div class="hstory-nav">
    <button class="hstory-arrow" id="hs-prev" onclick="hsPrev()" disabled>← Previous</button>
    <div>
      <div class="hstory-dots" id="hs-dots"></div>
      <div class="hstory-counter" style="text-align:center;margin-top:6px;" id="hs-counter">1 of 4</div>
    </div>
    <button class="hstory-arrow" id="hs-next" onclick="hsNext()">Next →</button>
  </div>
</div>

<script>
(function(){
  const track = document.getElementById("htrack");
  const panels = track.querySelectorAll(".hstory-panel");
  const dotsWrap = document.getElementById("hs-dots");
  const counter = document.getElementById("hs-counter");
  const prevBtn = document.getElementById("hs-prev");
  const nextBtn = document.getElementById("hs-next");
  let current = 0;
  const n = panels.length;

  // Build dots
  for(let i=0;i<n;i++){
    const d=document.createElement("button");
    d.className="hstory-dot"+(i===0?" active":"");
    d.onclick=()=>goTo(i);
    dotsWrap.appendChild(d);
  }

  function goTo(idx){
    current=idx;
    track.scrollTo({left:track.clientWidth*idx,behavior:"smooth"});
    dotsWrap.querySelectorAll(".hstory-dot").forEach((d,i)=>d.classList.toggle("active",i===idx));
    counter.textContent=(idx+1)+" of "+n;
    prevBtn.disabled=idx===0;
    nextBtn.disabled=idx===n-1;
    // Animate bars when on panel 4
    if(idx===3) animateBars();
  }

  function hsPrev(){if(current>0)goTo(current-1);}
  function hsNext(){if(current<n-1)goTo(current+1);}
  window.hsPrev=hsPrev; window.hsNext=hsNext;

  // Drag / swipe
  let startX=0,dragging=false;
  track.addEventListener("mousedown",e=>{startX=e.clientX;dragging=true;});
  track.addEventListener("mousemove",e=>{if(!dragging)return;});
  track.addEventListener("mouseup",e=>{
    if(!dragging)return; dragging=false;
    const dx=e.clientX-startX;
    if(dx<-50&&current<n-1)goTo(current+1);
    else if(dx>50&&current>0)goTo(current-1);
  });
  track.addEventListener("mouseleave",()=>{dragging=false;});

  // Count up 34
  let counted=false;
  const el34=document.getElementById("hs-34");
  const obs=new IntersectionObserver(entries=>{
    entries.forEach(e=>{
      if(e.isIntersecting&&!counted){
        counted=true;
        let v=0,target=34;
        const t=setInterval(()=>{v++;el34.textContent=v;if(v>=target)clearInterval(t);},40);
      }
    });
  },{threshold:0.3});
  if(el34)obs.observe(el34);

  function animateBars(){
    document.querySelectorAll("#hs-bars .hs-bar").forEach(b=>{
      const h=b.dataset.h+"px";
      setTimeout(()=>{b.style.transition="height 0.8s cubic-bezier(0.34,1.2,0.64,1)";b.style.height=h;},100);
    });
  }
})();
</script>
```

<div class="section-title">Your Personal Calculator</div>
<div class="section-subtitle">Enter your income and a state to see your personal rent burden.</div>

```{=html}
<div class="tool-dark">
  <div class="tool-title">Student Housing Affordability Calculator</div>
  <div class="tool-subtitle">Enter your annual income and pick a state to see your personal rent burden</div>
  <div class="tool-inputs">
    <div class="tool-ig"><label>Annual Income ($)</label><input type="number" id="ci" placeholder="e.g. 28000"/></div>
    <div class="tool-ig"><label>Select a State</label><select id="cs"><option value="">Choose a state...</option></select></div>
  </div>
  <button class="tool-btn" onclick="runCalc()">Calculate</button>
  <div class="result-box" id="rg">
    <div style="text-align:center"><div id="cg"></div></div>
    <div style="margin-top:12px;">
      <div id="rv" style="font-size:0.95em;line-height:1.7;margin-bottom:6px;"></div>
      <div id="rl" style="font-size:0.78em;opacity:0.5;"></div>
    </div>
  </div>
</div>
<script>
const csel=document.getElementById("cs");
Object.keys(CRD).sort().forEach(s=>{const o=document.createElement("option");o.value=s;o.textContent=s;csel.appendChild(o);});
function runCalc(){
  const income=parseFloat(document.getElementById("ci").value);
  const state=document.getElementById("cs").value;
  const gDiv=document.getElementById("rg");
  if(!income||income<=0||!state){gDiv.style.display="block";document.getElementById("rv").innerHTML="<span style='color:#d97706'>Please enter income and select a state.</span>";document.getElementById("rl").textContent="";document.getElementById("cg").innerHTML="";return;}
  const rent=CRD[state];
  const ratio=parseFloat(((rent/income)*100).toFixed(1));
  gDiv.style.display="block";
  let v;
  if(ratio<30)v="At <strong>"+ratio+"%</strong> of your income on rent in "+state+", you fall below the 30% threshold.";
  else if(ratio<50)v="In "+state+", <strong>"+ratio+"%</strong> of your income goes to rent. That leaves less than 70 cents of every dollar for everything else.";
  else v="In "+state+", a staggering <strong>"+ratio+"%</strong> of your income would go to rent — a crisis-level burden.";
  document.getElementById("rv").innerHTML=v;
  document.getElementById("rl").textContent="Median annual rent in "+state+": $"+rent.toLocaleString()+" (ACS 2023)";
  drawGauge(ratio,"cg");
}
</script>
```

<div class="section-title" id="should-i-go-there">Should I Go There?</div>
<div class="section-subtitle">Pick a college and your income to see if you can afford to live there, plus alternatives.</div>

```{=html}
<div class="tool-slate">
  <div class="tool-title">Should I Go There?</div>
  <div class="tool-subtitle">Your rent burden at that college's state, plus the most affordable alternatives on your income.</div>
  <div class="tool-inputs">
    <div class="tool-ig"><label>Annual Income ($)</label><input type="number" id="fi" placeholder="e.g. 28000"/></div>
    <div class="tool-ig"><label>Select a University</label><select id="fu"><option value="">Choose a university...</option></select></div>
  </div>
  <button class="tool-btn" onclick="runFinder()">Check</button>
  <div class="result-box" id="finder-result"></div>
</div>
<script>
document.addEventListener("DOMContentLoaded",function(){
  const s=document.getElementById("fu");
  Object.keys(UD).sort().forEach(u=>{const o=document.createElement("option");o.value=u;o.textContent=u+" ("+UD[u].state+")";s.appendChild(o);});
});
function runFinder(){
  const income=parseFloat(document.getElementById("fi").value);
  const uni=document.getElementById("fu").value;
  const res=document.getElementById("finder-result");
  if(!income||income<=0||!uni){res.style.display="block";res.innerHTML="<span style='color:#d97706'>Please enter income and select a university.</span>";return;}
  const d=UD[uni];
  const ratio=parseFloat(((d.rent/income)*100).toFixed(1));
  const color=ratio<30?"#059669":ratio<50?"#d97706":"#dc2626";
  const bg=ratio<30?"rgba(5,150,105,0.12)":ratio<50?"rgba(217,119,6,0.12)":"rgba(220,38,38,0.12)";
  let verdict;
  if(ratio<30)verdict="You can afford to live near <strong>"+uni+"</strong>. At "+ratio+"% of your income on rent in "+d.state+", you are below the threshold.";
  else if(ratio<50)verdict="Living near <strong>"+uni+"</strong> would be a stretch — "+ratio+"% of your income to rent in "+d.state+".";
  else verdict="Living near <strong>"+uni+"</strong> is financially unsustainable. "+ratio+"% of your income would go to rent in "+d.state+".";
  const alts=Object.entries(UD).filter(([nm,dt])=>(dt.rent/income)*100<30&&nm!==uni).map(([nm,dt])=>({nm,state:dt.state,ratio:parseFloat(((dt.rent/income)*100).toFixed(1))})).sort((a,b)=>a.ratio-b.ratio).slice(0,5);
  let altHTML="";
  if(ratio>=30&&alts.length>0){altHTML="<div style='margin-top:14px;padding-top:14px;border-top:1px solid rgba(255,255,255,0.1);'><div style='font-size:0.8em;font-weight:600;margin-bottom:8px;opacity:0.7;text-transform:uppercase;letter-spacing:0.05em;'>Affordable alternatives</div>"+alts.map(a=>"<div style='display:flex;justify-content:space-between;align-items:center;padding:7px 11px;background:rgba(5,150,105,0.1);border-radius:6px;margin-bottom:4px;font-size:0.85em;'><span><strong>"+a.nm+"</strong> <span style='opacity:0.55;'>("+a.state+")</span></span><span style='color:#34d399;font-weight:700;'>"+a.ratio+"%</span></div>").join("")+"</div>";}
  else if(ratio<30){altHTML="<div style='margin-top:10px;opacity:0.6;font-size:0.85em;'>Your income works well in this state.</div>";}
  else{altHTML="<div style='margin-top:10px;opacity:0.55;font-size:0.85em;'>No universities in our list fall below 30% on your income.</div>";}
  res.style.display="block";
  res.innerHTML="<div style='background:"+bg+";border-radius:10px;padding:18px;'><div style='font-size:1.8em;font-weight:800;color:"+color+";margin-bottom:6px;'>"+ratio+"% rent burden</div><div style='line-height:1.7;margin-bottom:6px;font-size:0.9em;'>"+verdict+"</div><div style='font-size:0.78em;opacity:0.45;'>Median annual rent in "+d.state+": $"+d.rent.toLocaleString()+" (ACS 2023)</div>"+altHTML+"</div>";
}
</script>
```

<div class="section-title" id="state-vs-state">State vs State</div>
<div class="section-subtitle">Pick any two states and get a head to head breakdown.</div>

```{=html}
<div class="tool-dark">
  <div class="tool-title">State vs State</div>
  <div class="tool-subtitle">Which state is actually better for a young renter?</div>
  <div class="tool-inputs">
    <div class="tool-ig"><label>State A</label><select id="vsa"><option value="">Choose state A...</option></select></div>
    <div class="tool-ig" style="flex:0;align-self:flex-end;"><div style="padding:12px 6px;opacity:0.35;font-weight:700;">vs</div></div>
    <div class="tool-ig"><label>State B</label><select id="vsb"><option value="">Choose state B...</option></select></div>
    <div style="align-self:flex-end;"><button class="tool-btn" onclick="runVS()">Compare</button></div>
  </div>
  <div class="result-box" id="vs-result">
    <div class="vs-cards">
      <div class="vs-card" id="vs-card-a"></div>
      <div><div class="vs-vs">vs</div><div id="vs-winner-tag" style="font-size:0.72em;color:#34d399;font-weight:700;text-align:center;margin-top:6px;"></div></div>
      <div class="vs-card" id="vs-card-b"></div>
    </div>
    <div class="vs-verdict" id="vs-verdict"></div>
  </div>
</div>
<script>
document.addEventListener("DOMContentLoaded",function(){
  const sa=document.getElementById("vsa"),sb=document.getElementById("vsb");
  Object.keys(VSD).sort().forEach(s=>{[sa,sb].forEach(el=>{const o=document.createElement("option");o.value=s;o.textContent=s;el.appendChild(o);});});
});
function vsC(b){return b<30?"#059669":b<50?"#d97706":"#dc2626";}
function runVS(){
  const sa=document.getElementById("vsa").value,sb=document.getElementById("vsb").value;
  const res=document.getElementById("vs-result");
  if(!sa||!sb||sa===sb){res.style.display="block";document.getElementById("vs-card-a").innerHTML="<div style='color:#d97706'>Please select two different states.</div>";document.getElementById("vs-card-b").innerHTML="";document.getElementById("vs-verdict").innerHTML="";document.getElementById("vs-winner-tag").textContent="";return;}
  const a=VSD[sa],b=VSD[sb],aW=a.burden<b.burden;
  const cH=(state,d)=>"<div class='vs-state-name'>"+state+"</div><div class='vs-big-pct' style='color:"+vsC(d.burden)+";'>"+d.burden+"%</div><div style='font-size:0.72em;opacity:0.55;margin-bottom:8px;'>rent burden (under-25)</div><div class='vs-metric'><strong>Annual Rent:</strong> $"+d.rent.toLocaleString()+"<br><strong>Under-25 Income:</strong> $"+d.income.toLocaleString()+"<br><strong>Category:</strong> "+d.cat+"</div>";
  document.getElementById("vs-card-a").className="vs-card"+(aW?" winner":"");
  document.getElementById("vs-card-b").className="vs-card"+(!aW?" winner":"");
  document.getElementById("vs-card-a").innerHTML=cH(sa,a);
  document.getElementById("vs-card-b").innerHTML=cH(sb,b);
  document.getElementById("vs-winner-tag").textContent=(aW?sa:sb)+" wins";
  const w=aW?a:b,l=aW?b:a,wn=aW?sa:sb,ln=aW?sb:sa;
  document.getElementById("vs-verdict").innerHTML="<strong>"+wn+"</strong> is the more affordable state, with a "+w.burden+"% burden versus "+l.burden+"% in <strong>"+ln+"</strong> — a difference of "+Math.abs(a.burden-b.burden).toFixed(1)+" percentage points.";
  res.style.display="block";
}
</script>
```

<div class="section-title" id="rent-burden-time-machine">Rent Burden Time Machine</div>
<div class="section-subtitle">Pick a state and drag the slider to see how burden changed from 2015 to 2023.</div>

```{=html}
<div class="tm-wrap">
  <div class="tool-title">Rent Burden Time Machine</div>
  <div class="tool-subtitle">2020 data was not collected due to COVID-19 collection disruptions.</div>
  <div class="tool-inputs">
    <div class="tool-ig"><label>Select a State</label><select id="tm-state"><option value="">Choose a state...</option></select></div>
  </div>
  <div id="tm-result" style="display:none;">
    <div id="tm-year-label" style="font-size:2em;font-weight:800;margin-bottom:4px;"></div>
    <div id="tm-burden-label" style="font-size:0.88em;opacity:0.6;margin-bottom:16px;"></div>
    <input type="range" id="tm-slider" min="0" max="7" value="7" step="1"
      style="width:100%;accent-color:#2563eb;height:5px;cursor:pointer;" oninput="updateTM()"/>
    <div style="display:flex;justify-content:space-between;font-size:0.72em;opacity:0.4;margin-top:5px;">
      <span>2015</span><span>2016</span><span>2017</span><span>2018</span><span>2019</span><span>2021</span><span>2022</span><span>2023</span>
    </div>
    <div style="background:rgba(255,255,255,0.04);border-radius:10px;padding:16px;margin-top:16px;">
      <svg id="tm-svg" width="100%" height="160" viewBox="0 0 600 160" preserveAspectRatio="xMidYMid meet"></svg>
    </div>
    <div id="tm-trend-text" style="margin-top:12px;font-size:0.85em;line-height:1.7;opacity:0.7;"></div>
  </div>
</div>
<script>
document.addEventListener("DOMContentLoaded",function(){
  const s=document.getElementById("tm-state");
  Object.keys(TMD).sort().forEach(st=>{const o=document.createElement("option");o.value=st;o.textContent=st;s.appendChild(o);});
  s.addEventListener("change",function(){
    if(this.value){document.getElementById("tm-result").style.display="block";document.getElementById("tm-slider").value=7;updateTM();}
    else document.getElementById("tm-result").style.display="none";
  });
});
function updateTM(){
  const state=document.getElementById("tm-state").value;if(!state)return;
  const d=TMD[state],idx=parseInt(document.getElementById("tm-slider").value);
  const burden=d.burdens[idx],year=d.years[idx],color=getColor(burden);
  document.getElementById("tm-year-label").innerHTML="<span style='color:"+color+";'>"+burden.toFixed(1)+"%</span> in "+year;
  document.getElementById("tm-burden-label").textContent=state+" — under-25 rent burden";
  const svg=document.getElementById("tm-svg"),W=600,H=140,P=36;
  const minB=Math.min(...d.burdens)-2,maxB=Math.max(...d.burdens)+2;
  const xS=i=>P+(i/(d.years.length-1))*(W-P*2);
  const yS=b=>H-P-(b-minB)/(maxB-minB)*(H-P*1.4);
  let path="";d.years.forEach((y,i)=>{path+=(i===0?"M":"L")+xS(i)+","+yS(d.burdens[i]);});
  let dots="";d.years.forEach((y,i)=>{
    const c=i===idx?"#2563eb":"rgba(255,255,255,0.3)",r=i===idx?5:2.5;
    dots+=`<circle cx="${xS(i)}" cy="${yS(d.burdens[i])}" r="${r}" fill="${c}" stroke="white" stroke-width="1.2"/>`;
  });
  const tY=yS(30);
  svg.innerHTML=`<line x1="${P}" y1="${tY}" x2="${W-P}" y2="${tY}" stroke="rgba(5,150,105,0.35)" stroke-width="1" stroke-dasharray="4"/><text x="${P+4}" y="${tY-4}" font-size="8" fill="rgba(5,150,105,0.6)">30% threshold</text><path d="${path}" fill="none" stroke="rgba(255,255,255,0.45)" stroke-width="2" stroke-linejoin="round"/>${dots}<circle cx="${xS(idx)}" cy="${yS(d.burdens[idx])}" r="7" fill="${getColor(d.burdens[idx])}" stroke="white" stroke-width="2"/>`;
  const first=d.burdens[0],last=d.burdens[d.burdens.length-1],ch=(last-first).toFixed(1);
  const dir=ch>0?"increased by "+Math.abs(ch)+" pp":"decreased by "+Math.abs(ch)+" pp";
  document.getElementById("tm-trend-text").innerHTML="From 2015 to 2023, rent burden in <strong>"+state+"</strong> <strong>"+dir+"</strong>, from "+first.toFixed(1)+"% to "+last.toFixed(1)+"%.";
}
</script>
```

<div class="section-title">All 51 States Ranked</div>
<div class="section-subtitle">Hover any bar for full details. Sorted from most to least burdened.</div>

```{r}
#| label: all-states
#| echo: false
#| message: false
#| warning: false
#| fig-height: 14

COLORS <- c("Affordable"="#059669","Burdened"="#d97706","Severely Burdened"="#dc2626")
p5 <- ggplot(burden_2023,
  aes(x=fct_reorder(State,burden_under25),y=burden_under25,fill=burden_cat_under25,
      text=paste0("<b>",State,"</b><br>Burden: ",round(burden_under25,1),"%<br>Category: ",burden_cat_under25,"<br>Annual Rent: $",format(round(median_rent_annual),big.mark=","),"<br>Income (Under-25): $",format(round(income_under25),big.mark=","))))+
  geom_col(width=0.75,alpha=0.88)+
  geom_hline(yintercept=30,linetype="dashed",color="#0f1f3d",linewidth=0.6,alpha=0.5)+
  geom_hline(yintercept=50,linetype="dashed",color="#dc2626",linewidth=0.6,alpha=0.5)+
  coord_flip()+
  scale_fill_manual(values=COLORS,name="Burden Category")+
  scale_y_continuous(labels=label_percent(scale=1))+
  labs(x=NULL,y="Rent Burden Ratio (%)")+
  theme_minimal(base_size=11)+
  theme(axis.text.y=element_text(size=8),legend.position="top",panel.grid.minor=element_blank(),panel.grid.major.y=element_blank())

ggplotly(p5,tooltip="text",height=900)%>%
  layout(legend=list(orientation="h",x=0,y=1.02),font=list(family="sans-serif"),margin=list(l=120))
```

```{=html}
<div class="conclusion-wrap" id="conclusion">
  <h2>What This Means</h2>
  <p class="sub">Four conclusions grounded in the data.</p>
  <div class="conc-grid">
    <div class="conc-card" style="border-color:#2563eb;">
      <h4>College choice is a housing decision</h4>
      <p>California (48.3%), Hawaii (47.8%), and Florida (44.1%) are the most popular college destinations and the least affordable states for young renters. Where you study determines how much of your income disappears into rent.</p>
    </div>
    <div class="conc-card" style="border-color:#d97706;">
      <h4>The income gap is the real problem</h4>
      <p>Young renters are not paying dramatically higher rents than older adults. They are paying similar rents on dramatically lower incomes. The 2x burden gap is entirely an income gap, not a rent gap.</p>
    </div>
    <div class="conc-card" style="border-color:#059669;">
      <h4>Affordable states are not accessible</h4>
      <p>Wyoming (23.3%) and North Dakota (24.0%) offer the lowest burden ratios. But they also have the fewest universities and least opportunity. Affordability and access rarely appear in the same state.</p>
    </div>
    <div class="conc-card" style="border-color:#818cf8;">
      <h4>This gap will not resolve itself</h4>
      <p>The burden peaks during the exact years when young people are making foundational decisions about college, careers, and cities. Every under-25 renter today is navigating a system not designed with their income in mind.</p>
    </div>
  </div>
  <div class="final-stmt">
    In 2023, <strong>34 out of 51 states</strong> cost-burdened young renters. <strong>Zero</strong> did the same to established adults. The data describes not a universal housing crisis but a generational fault line — where the same economy that works for adults aged 25 to 44 systematically fails adults under 25.
  </div>
</div>

<div style="background:#f8fafc;border-radius:12px;padding:20px;margin:24px 0;font-size:0.82em;color:#64748b;line-height:1.8;border:1px solid #e2e8f0;">
  <strong style="color:#0f1f3d;">Data Sources</strong><br>
  Income by Age: ACS 1-Year Estimates Table B19049 (2015-2023, excl. 2020) &nbsp;·&nbsp;
  Median Gross Rent: ACS 1-Year Estimates Table B25064 (2015-2023, excl. 2020) &nbsp;·&nbsp;
  Historical Income: CPS Historical Income Table H-8 (1984-2024)<br>
  Data via tidycensus R package. Puerto Rico excluded. 2020 ACS not released due to COVID-19.<br>
  Analysis: Elma M., Jack D., Thusa &nbsp;·&nbsp; COMP/STAT 212, Macalester College, Spring 2026.
</div>
```


```{=html}
<script>
window.addEventListener("load", function() {
  setTimeout(function() {

    function fillSelect(id, data, placeholder, labelFn) {
      const select = document.getElementById(id);
      if (!select || typeof data === "undefined") return;

      select.innerHTML = "";

      const first = document.createElement("option");
      first.value = "";
      first.textContent = placeholder;
      select.appendChild(first);

      Object.keys(data).sort().forEach(function(key) {
        const option = document.createElement("option");
        option.value = key;
        option.textContent = labelFn ? labelFn(key, data[key]) : key;
        select.appendChild(option);
      });
    }

    if (typeof CRD !== "undefined") {
      fillSelect("cs", CRD, "Choose a state...");
    }

    if (typeof UD !== "undefined") {
      fillSelect("fu", UD, "Choose a university...", function(key, value) {
        return key + " (" + value.state + ")";
      });
    }

    if (typeof VSD !== "undefined") {
      fillSelect("vsa", VSD, "Choose state A...");
      fillSelect("vsb", VSD, "Choose state B...");
    }

    if (typeof TMD !== "undefined") {
      fillSelect("tm-state", TMD, "Choose a state...");

      const tm = document.getElementById("tm-state");
      if (tm) {
        tm.addEventListener("change", function() {
          if (this.value) {
            document.getElementById("tm-result").style.display = "block";
            document.getElementById("tm-slider").value = 7;
            updateTM();
          } else {
            document.getElementById("tm-result").style.display = "none";
          }
        });
      }
    }

  }, 300);
});
</script>
```


```{=html}
<script>
window.addEventListener("load", function() {
  setTimeout(function() {
    function refillSelect(id, data, placeholder, labelFn) {
      const select = document.getElementById(id);
      if (!select || typeof data === "undefined") return;

      // Refill only if the dropdown has no real options.
      if (select.options.length > 1) return;

      select.innerHTML = "";
      const first = document.createElement("option");
      first.value = "";
      first.textContent = placeholder;
      select.appendChild(first);

      Object.keys(data).sort().forEach(function(key) {
        const opt = document.createElement("option");
        opt.value = key;
        opt.textContent = labelFn ? labelFn(key, data[key]) : key;
        select.appendChild(opt);
      });
    }

    if (typeof CRD !== "undefined") {
      refillSelect("cs", CRD, "Choose a state...");
    }

    if (typeof UD !== "undefined") {
      refillSelect("fu", UD, "Choose a university...", function(key, value) {
        return key + " (" + value.state + ")";
      });
    }

    if (typeof VSD !== "undefined") {
      refillSelect("vsa", VSD, "Choose state A...");
      refillSelect("vsb", VSD, "Choose state B...");
    }

    if (typeof TMD !== "undefined") {
      refillSelect("tm-state", TMD, "Choose a state...");
    }
  }, 400);
});
</script>
```
