---
title: "Thusa"
subtitle: "College-Age Renter Affordability: Early Data Exploration"
format: 
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    fig-width: 10
    fig-height: 8
    embed-resources: true
execute: 
  warning: false
  message: false
---

## 1. Overview & Research Questions

This notebook explores housing affordability for college-age renters using American Community Survey (ACS) data accessed via `tidycensus`. We examine three core questions:

1. **Which U.S. states are most and least affordable for college-age renters (18–24), and how does this compare to older age groups?**
2. **What is the rent-to-income burden ratio for 18–24 year-olds by state, and how many states fall into "affordable" (\<30%), "burdened" (30–50%), or "severely burdened" (\>50%) categories?**
3. **How has the affordability gap between younger renters (18–24) and established adults (35–44) changed over recent years, and which states show the most significant generational disparities in housing costs?**

### Data Sources & Important Caveats

- **ACS Table B19049**: Median household income by age of householder.
- **ACS Table B25064**: Median gross rent (dollars).
- **Age Proxies**: ACS uses brackets 15–24, 25–44, 45–64, and 65+. We use **15–24** as the closest available proxy for the college-age (18–24) cohort and **25–44** as the proxy for established adults (35–44).
- **Householder vs. Individual**: These tables report income for the *householder* (the person who owns or rents the home). College students living in dorms or with parents are typically not householders and are therefore not captured in these household-level estimates. This is a standard limitation of Census household data for college-age affordability research.

---

## 2. Setup & Configuration

```{r}
#| label: setup
#| echo: true

library(tidycensus)
library(tidyverse)
library(scales)

# Census API Key

census_api_key("d6ea3b74acd33e1a166357b8af8134055725a821", install = TRUE, overwrite = TRUE)

# Analysis Parameters 
YEARS       <- 2010:2023                   # Years to analyze
SURVEY      <- "acs5"                      # "acs1" (1-year) or "acs5" (5-year)
STATE_FIPS  <- NULL                        # NULL = all states + DC

# HUD affordability thresholds
THRESH_AFFORDABLE <- 30
THRESH_BURDENED   <- 50
```

---

## 3. Data Ingestion

We pull state-level ACS estimates for median household income by age of householder (B19049) and median gross rent (B25064).

```{r}
#| label: define-variables

# B19049: Median Household Income by Age of Householder
income_vars <- c(
  medinc_total   = "B19049_001",  # All ages
  medinc_15_24   = "B19049_002",  # Householder 15 to 24 years
  medinc_25_44   = "B19049_003",  # Householder 25 to 44 years
  medinc_45_64   = "B19049_004",  # Householder 45 to 64 years
  medinc_65_plus = "B19049_005"   # Householder 65 years and over
)

# B25064: Median Gross Rent (monthly dollars)
rent_vars <- c(med_rent = "B25064_001")

# head(income_vars)
```


```{r}
#| label: pull-data
#| message: true

pull_state_data <- function(year, survey = "acs5") {
  
  message("Pulling data for ", year, " ...")
  
  # Income data (wide format)
  income_df <- get_acs(
    geography = "state",
    variables = income_vars,
    year = year,
    survey = survey,
    output = "wide",
    state = STATE_FIPS
  ) %>%
    mutate(year = year)
  
  # Rent data — same fix applied
  rent_df <- get_acs(
    geography = "state",
    variables = rent_vars,
    year = year,
    survey = survey,
    output = "wide",
    state = STATE_FIPS
  ) %>%
    mutate(year = year)
  
  # Merge
  full_df <- income_df %>%
    left_join(rent_df, by = c("GEOID", "NAME", "year"))
  
  return(full_df)
}

# Pull all years and combine
raw_data <- map_dfr(YEARS, ~ pull_state_data(.x, SURVEY))
#names(raw_data)
```

```{r}
#| label: clean-and-validate
#| echo: true

# Inspect structure
glimpse(raw_data)

# Check column names
print(names(raw_data))

# Clean and standardize
clean_data <- raw_data %>%
  rename(state = NAME) %>%
  mutate(
    across(
      c(med_rentE, starts_with("medinc")),
      as.numeric
    )
  )

# Check missing values
missing_summary <- clean_data %>%
  summarise(
    across(
      c(med_rentE, starts_with("medinc")),
      ~ sum(is.na(.))
    )
  )

print(missing_summary)

# Filter out problematic rows
clean_data <- clean_data %>%
  filter(
    !is.na(med_rentE),
    !is.na(medinc_15_24E),
    medinc_15_24E > 0
  )

# Final sanity check
clean_data %>%
  select(state, year, med_rentE, medinc_15_24E) %>%
  head(10)
```

---

## 4. Calculate Burden Metrics

We annualize rent (ACS reports monthly rent; income is annual), compute rent-to-income ratios for each age bracket, assign HUD burden categories, and calculate the generational affordability gap.

```{r}
#| label: calculate-metrics
#| echo: true

analysis_df <- clean_data %>%
  mutate(
    # Annualize rent
    annual_rent = med_rentE * 12,
    
    # Rent-to-income ratios (%)
    rtb_15_24 = (annual_rent / medinc_15_24E) * 100,
    rtb_25_44 = (annual_rent / medinc_25_44E) * 100,
    
    # Affordability categories (young renters)
    burden_cat_young = case_when(
      rtb_15_24 < THRESH_AFFORDABLE ~ "Affordable (<30%)",
      rtb_15_24 <= THRESH_BURDENED  ~ "Burdened (30-50%)",
      TRUE                          ~ "Severely Burdened (>50%)"
    ) %>% factor(levels = c(
      "Affordable (<30%)", 
      "Burdened (30-50%)", 
      "Severely Burdened (>50%)"
    )),
    
    # Affordability categories (older group)
    burden_cat_established = case_when(
      rtb_25_44 < THRESH_AFFORDABLE ~ "Affordable (<30%)",
      rtb_25_44 <= THRESH_BURDENED  ~ "Burdened (30-50%)",
      TRUE                          ~ "Severely Burdened (>50%)"
    ) %>% factor(levels = c(
      "Affordable (<30%)", 
      "Burdened (30-50%)", 
      "Severely Burdened (>50%)"
    )),
    
    # Generational gap
    affordability_gap = rtb_15_24 - rtb_25_44
  )

# Quick Check
analysis_df %>%
  select(state, year, rtb_15_24, rtb_25_44) %>%
  head(10)
```

---

## 5. Q1: Most & Least Affordable States for Young Renters

We rank states by the rent-to-income burden for the 15–24 age bracket (our proxy for 18–24) using the most recent year of data.

```{r}
#| label: q1-rankings
#| echo: true

latest_year <- max(analysis_df$year)

q1_rankings <- analysis_df %>%
  filter(year == latest_year) %>%
  select(
    state,
    rtb_15_24,
    rtb_25_44,
    affordability_gap,
    med_rentE
  ) %>%
  arrange(rtb_15_24)
```

### Most Affordable (Lowest Burden)

```{r}
#| label: q1-most-affordable

head(q1_rankings, 10)
```

### Least Affordable (Highest Burden)

```{r}
#| label: q1-least-affordable

tail(q1_rankings, 10)
```

---

## 6. Q2: Burden Categories for 18–24 Year-Olds

We classify each state into HUD affordability categories based on the young renter burden ratio and tally the results.

### Summary Counts

```{r}
#| label: q2-summary

q2_summary <- analysis_df %>%
  filter(year == latest_year) %>%
  count(burden_cat_young, name = "num_states") %>%
  mutate(pct_states = round((num_states / sum(num_states)) * 100, 1))

q2_summary
```

### States by Category

```{r}
#| label: q2-by-state

q2_by_state <- analysis_df %>%
  filter(year == latest_year) %>%
  select(state, rtb_15_24, burden_cat_young) %>%
  arrange(burden_cat_young, desc(rtb_15_24))

q2_by_state
```

---

## 7. Q3: Trends & Generational Disparities

If multiple years are selected, we examine how the national affordability gap has evolved and identify states with the largest disparities.

### National Gap Trend

```{r}
#| label: q3-gap-trend
#| echo: true

gap_trend <- analysis_df %>%
  group_by(year) %>%
  summarise(
    mean_gap   = mean(affordability_gap, na.rm = TRUE),
    median_gap = median(affordability_gap, na.rm = TRUE),
    max_gap    = max(affordability_gap, na.rm = TRUE),
    min_gap    = min(affordability_gap, na.rm = TRUE),
    .groups = "drop"
  )

gap_trend
```

### States with Largest Generational Gaps (Most Recent Year)

```{r}
#| label: q3-largest-gaps
#| eval: !expr length(YEARS) > 1

largest_gaps <- analysis_df %>%
  filter(year == latest_year) %>%
  arrange(desc(affordability_gap)) %>%
  select(
    state = state, 
    affordability_gap, 
    rtb_15_24, 
    rtb_25_44, 
    med_rentE
  ) %>%
  head(10)

largest_gaps
```

### States Where the Gap Has Widened Most

```{r}
#| label: q3-gap-change
#| eval: !expr length(YEARS) > 1

gap_change <- analysis_df %>%
  select(year, state = state, affordability_gap) %>%
  filter(year %in% c(min(YEARS), max(YEARS))) %>%
  pivot_wider(
    names_from = year, 
    values_from = affordability_gap, 
    names_prefix = "yr_"
  ) %>%
  mutate(
    gap_change = !!sym(paste0("yr_", max(YEARS))) - !!sym(paste0("yr_", min(YEARS)))
  ) %>%
  arrange(desc(gap_change))

head(gap_change, 10)
```

---

## 8. Visualizations

### Burden by State (Ranked Bar Chart)

```{r}
#| label: fig-burden-ranking
#| fig-cap: "Rent-to-income burden for young renters (15–24) by state. Dashed lines show the 30% and 50% HUD thresholds."

p1 <- analysis_df %>%
  filter(year == latest_year) %>%
  mutate(state = fct_reorder(state, rtb_15_24)) %>%
  ggplot(aes(x = rtb_15_24, y = state, fill = burden_cat_young)) +
  geom_col(width = 0.7) +
  geom_vline(
    xintercept = THRESH_AFFORDABLE, 
    linetype = "dashed", 
    color = "darkorange", 
    linewidth = 0.8
  ) +
  geom_vline(
    xintercept = THRESH_BURDENED, 
    linetype = "dashed", 
    color = "firebrick", 
    linewidth = 0.8
  ) +
  scale_fill_manual(values = c(
    "Affordable (<30%)"        = "#2ca02c",
    "Burdened (30-50%)"        = "#ff7f0e",
    "Severely Burdened (>50%)" = "#d62728"
  )) +
  scale_x_continuous(
    labels = percent_format(scale = 1), 
    expand = c(0, 0)
  ) +
  labs(
    title    = paste(
      "Rent-to-Income Burden for Young Renters by State (", 
      latest_year, 
      ")", 
      sep = ""
    ),
    subtitle = "Young renters = householders aged 15–24 (proxy for 18–24 college-age cohort)",
    x        = "Rent-to-Income Ratio (%)",
    y        = NULL,
    fill     = "Affordability Category",
    caption  = paste(
      "Data: ACS", 
      ifelse(SURVEY == "acs1", "1-Year", "5-Year"), 
      "Estimates via tidycensus.\nRed line = 50% (severely burdened); Orange line = 30% (burdened threshold)."
    )
  ) +
  theme_minimal(base_size = 11) +
  theme(
    legend.position      = "bottom",
    panel.grid.major.y   = element_blank(),
    panel.grid.minor     = element_blank()
  )

p1
```

### Young vs. Established Adults: Scatter Comparison

```{r}
#| label: fig-scatter-comparison
#| fig-cap: "Comparison of rent burden between young renters (15–24) and established adults (25–44). Points above the diagonal indicate worse affordability for younger renters."

p2 <- analysis_df %>%
  filter(year == latest_year) %>%
  ggplot(aes(x = rtb_25_44, y = rtb_15_24)) +
  geom_abline(
    slope = 1, 
    intercept = 0, 
    linetype = "dashed", 
    color = "gray60"
  ) +
  geom_point(
    aes(size = med_rentE, color = affordability_gap), 
    alpha = 0.85
  ) +
  geom_text(
    aes(label = state), 
    check_overlap = TRUE, 
    size = 2.8, 
    vjust = -0.8, 
    fontface = "bold"
  ) +
  scale_color_gradient2(
    low      = "steelblue",
    mid      = "white",
    high     = "firebrick",
    midpoint = 0,
    name     = "Gap (pp)"
  ) +
  scale_size_continuous(
    range = c(2, 8), 
    name = "Median Rent ($)"
  ) +
  labs(
    title    = "Young Renters vs. Established Adults: Rent Burden by State",
    subtitle = paste(
      "Above diagonal = worse for young renters (", 
      latest_year, 
      ")", 
      sep = ""
    ),
    x        = "Rent-to-Income Ratio: 25–44 years (%)",
    y        = "Rent-to-Income Ratio: 15–24 years (%)",
    caption  = "Diagonal line indicates equal burden. Points above = generational disparity favoring older renters."
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "right")

p2
```

### National Gap Trend Over Time

```{r}
#| label: fig-gap-trend
#| fig-cap: "National trend in the mean affordability gap between young and established renters."
#| eval: !expr length(YEARS) > 1

p3 <- gap_trend %>%
  ggplot(aes(x = year, y = mean_gap)) +
  geom_line(color = "steelblue", linewidth = 1.2) +
  geom_point(size = 3, color = "steelblue") +
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray50") +
  labs(
    title    = "National Trend: Affordability Gap Between Young and Established Renters",
    subtitle = "Mean difference in rent-to-income burden (15–24 minus 25–44)",
    x        = "Year",
    y        = "Mean Gap (percentage points)",
    caption  = "Positive values indicate younger renters face a higher housing cost burden."
  ) +
  theme_minimal(base_size = 11)

p3
```

---

## 9. Export Results

Uncomment the lines below to save the analysis dataset and figures to your working directory.

```{r}
#| label: export
#| eval: false

write_csv(analysis_df, "state_rent_burden_analysis.csv")
ggsave("burden_by_state.png", p1, width = 10, height = 12, dpi = 300)
ggsave("young_vs_established_scatter.png", p2, width = 10, height = 8, dpi = 300)
if (exists("p3")) ggsave("gap_trend.png", p3, width = 10, height = 6, dpi = 300)
```

